
```{r setup, include=FALSE}
source("CorrelationPlot.R")
library(sjPlot)
library(jtools)
library(nlme)
library(dplyr)
library(ggplot2)
library(lme4)
library(dotwhisker)
library(ggpubr)
library(stargazer)


PerStudy <- read.csv("/Users/annalangener/Nextcloud/BEHAPP data/PerStudy.csv")
PerWeek <- read.csv("/Users/annalangener/Nextcloud/BEHAPP data/PerWeek.csv")
PerDay <- read.csv("/Users/annalangener/Nextcloud/BEHAPP data/PerDay.csv")
PerHour <- read.csv("/Users/annalangener/Nextcloud/BEHAPP data/PerHour.csv")

to_analyze <- read.csv("/Users/annalangener/Google Drive/PhD Wellbeing/to_analyse.csv")
to_analyze <- to_analyze[,colnames(to_analyze) %in% c("BEHAPP_ID","SFS","Loneliness")]

PerStudy <- left_join(PerStudy, to_analyze, by = c("ParticipantNumber" = "BEHAPP_ID"),suffix = c("",""))
PerWeek <- left_join(PerWeek, to_analyze, by = c("ParticipantNumber" = "BEHAPP_ID"),suffix = c("",""))
PerDay <- left_join(PerDay, to_analyze, by = c("ParticipantNumber" = "BEHAPP_ID"),suffix = c("",""))
PerHour <- left_join(PerHour, to_analyze, by = c("ParticipantNumber" = "BEHAPP_ID"),suffix = c("",""))

set.seed(12361488)
train_ind <- sample(PerStudy$ParticipantNumber, size = 0.7*nrow(PerStudy))

PerHourtrain <- PerHour[PerHour$ParticipantNumber %in% train_ind, ]
PerHourtest <- PerHour[!PerHour$ParticipantNumber %in% train_ind, ]

PerDaytrain <- PerDay[PerDay$ParticipantNumber %in% train_ind, ]
PerDaytest <- PerDay[!PerDay$ParticipantNumber %in% train_ind, ]

PerWeektrain <- PerWeek[PerWeek$ParticipantNumber %in% train_ind, ]
PerWeektest <- PerWeek[!PerWeek$ParticipantNumber %in% train_ind, ]

PerStudytrain <- PerStudy[PerStudy$ParticipantNumber %in% train_ind, ]
PerStudytest <- PerStudy[!PerStudy$ParticipantNumber %in% train_ind, ]


# NA not replaced
PerHourNA <- PerHour
PerHourNA[is.na(PerHourNA)] <- 0
PerDayNA <- PerDay
PerDayNA[is.na(PerDayNA)] <- 0
PerWeekNA <- PerWeek
PerWeekNA[is.na(PerWeekNA)] <- 0
PerStudyNA <- PerStudy
PerStudyNA[is.na(PerStudyNA)] <- 0

```


### Correlations
0.1 Small
0.3 Moderate
0.5 Large

Cohen's (1988)
```{r echo=FALSE}
Correlation <- data.frame(Correlation = cor.test(PerHour[,"HOME"],PerHour$SFS)$estimate, p.value = round(cor.test(PerHour[,"HOME"],PerHour$SFS)$p.value,2), Feature = "HOME", Time = "Per Hour")

Correlation <- rbind(Correlation, data.frame(Correlation = cor.test(PerDay[,"HOME"],PerDay$SFS)$estimate, p.value = round(cor.test(PerDay[,"HOME"],PerDay$SFS)$p.value,2), Feature = "HOME", Time = "Per Day"))

Correlation <-  rbind(Correlation, data.frame(Correlation = cor.test(PerWeek[,"HOME"],PerWeek$SFS)$estimate, p.value = round(cor.test(PerWeek[,"HOME"],PerWeek$SFS)$p.value,2), Feature = "HOME", Time = "Per Week"))

Correlation <-  rbind(Correlation, data.frame(Correlation = cor.test(PerStudy[,"HOME"],PerStudy$SFS)$estimate, p.value = round(cor.test(PerStudy[,"HOME"],PerStudy$SFS)$p.value,2), Feature = "HOME", Time = "Per Study"))

Features <- c("TotalMinutes", "COMMUNICATION", "SOCIAL", "NumberOpened", "UniqueNumber", "TimeStationary")

for(i in 1:length(Features)){
  Correlation <- rbind(Correlation,data.frame(Correlation = cor.test(PerHour[,Features[i]],PerHour$SFS)$estimate, p.value = round(cor.test(PerHour[,Features[i]],PerHour$SFS)$p.value,2), Feature = Features[i], Time = "Per Hour"))
  
  Correlation <-  rbind(Correlation, data.frame(Correlation = cor.test(PerDay[,Features[i]],PerDay$SFS)$estimate, p.value = round(cor.test(PerDay[,Features[i]],PerDay$SFS)$p.value,2), Feature = Features[i], Time = "Per Day"))

Correlation <-  rbind(Correlation, data.frame(Correlation = cor.test(PerWeek[,Features[i]],PerWeek$SFS)$estimate, p.value = round(cor.test(PerWeek[,Features[i]],PerWeek$SFS)$p.value,2), Feature = Features[i], Time = "Per Week"))

Correlation <-  rbind(Correlation, data.frame(Correlation = cor.test(PerStudy[,Features[i]],PerStudy$SFS)$estimate, p.value = round(cor.test(PerStudy[,Features[i]],PerStudy$SFS)$p.value,2), Feature = Features[i], Time = "Per Study"))

}
```

```{r echo=FALSE}
Correlation <- data.frame(Correlation = cor.test(PerHour[,"HOME"],PerHour$LONELINESS)$estimate, p.value = round(cor.test(PerHour[,"HOME"],PerHour$LONELINESS)$p.value,2), Feature = "HOME", Time = "Per Hour")

Correlation <- rbind(Correlation, data.frame(Correlation = cor.test(PerDay[,"HOME"],PerDay$LONELINESS)$estimate, p.value = round(cor.test(PerDay[,"HOME"],PerDay$LONELINESS)$p.value,2), Feature = "HOME", Time = "Per Day"))

Correlation <-  rbind(Correlation, data.frame(Correlation = cor.test(PerWeek[,"HOME"],PerWeek$LONELINESS)$estimate, p.value = round(cor.test(PerWeek[,"HOME"],PerWeek$LONELINESS)$p.value,2), Feature = "HOME", Time = "Per Week"))

Correlation <-  rbind(Correlation, data.frame(Correlation = cor.test(PerStudy[,"HOME"],PerStudy$LONELINESS)$estimate, p.value = round(cor.test(PerStudy[,"HOME"],PerStudy$LONELINESS)$p.value,2), Feature = "HOME", Time = "Per Study"))

Features <- c("TotalMinutes", "COMMUNICATION", "SOCIAL", "NumberOpened", "HOME", "UniqueNumber", "TimeStationary")

for(i in 1:length(Features)){
  Correlation <- rbind(Correlation,data.frame(Correlation = cor.test(PerHour[,Features[i]],PerHour$LONELINESS)$estimate, p.value = round(cor.test(PerHour[,Features[i]],PerHour$LONELINESS)$p.value,2), Feature = Features[i], Time = "Per Hour"))
  
  Correlation <-  rbind(Correlation, data.frame(Correlation = cor.test(PerDay[,Features[i]],PerDay$LONELINESS)$estimate, p.value = round(cor.test(PerDay[,Features[i]],PerDay$LONELINESS)$p.value,2), Feature = Features[i], Time = "Per Day"))

Correlation <-  rbind(Correlation, data.frame(Correlation = cor.test(PerWeek[,Features[i]],PerWeek$LONELINESS)$estimate, p.value = round(cor.test(PerWeek[,Features[i]],PerWeek$LONELINESS)$p.value,2), Feature = Features[i], Time = "Per Week"))

Correlation <-  rbind(Correlation, data.frame(Correlation = cor.test(PerStudy[,Features[i]],PerStudy$LONELINESS)$estimate, p.value = round(cor.test(PerStudy[,Features[i]],PerStudy$LONELINESS)$p.value,2), Feature = Features[i], Time = "Per Study"))

}
```



```{r echo=FALSE}
### Being Home & Unique Number of Places Visited

#Correlation <- merge(CorPerHour,CorPerDay, by = "ParticipantNumber")
#Correlation <- merge(Correlation,CorPerWeek, by = "ParticipantNumber")

CorrelationSFS <- function(Feature){

print(cor.test(PerHour[,Feature],PerHour$SFS))
print(cor.test(PerDay[,Feature],PerDay$SFS))
print(cor.test(PerWeek[,Feature],PerWeek$SFS))
print(cor.test(PerStudy[,Feature],PerStudy$SFS))

print(cor.test(PerHourNA[,Feature],PerHourNA$SFS))
print(cor.test(PerDayNA[,Feature],PerDayNA$SFS))
print(cor.test(PerWeekNA[,Feature],PerWeekNA$SFS))
print(cor.test(PerStudyNA[,Feature],PerStudyNA$SFS))

plot1 <- ggplot() +
  geom_hline(yintercept=as.numeric(cor.test(PerHour[,Feature],PerHour$SFS)$estimate), linetype="dashed", color = "#0B3C69")  +
  geom_hline(yintercept=as.numeric(cor.test(PerDay[,Feature],PerDay$SFS)$estimate), linetype="dashed", color = "#708FF9") +
  geom_hline(yintercept=as.numeric(cor.test(PerWeek[,Feature],PerWeek$SFS)$estimate), linetype="dashed", color = "#FFCD3C") +
  geom_hline(yintercept=as.numeric(cor.test(PerStudy[,Feature],PerStudy$SFS)$estimate), linetype="dashed", color = "#FF5733") +
  ylab(element_blank()) +
  xlab("Participants") +
  scale_color_manual(name = "Resolution", values = c("Per Hour" = "#0B3C69", "Per Day" = "#708FF9", "Per Week" = "#FFCD3C"))+
  theme_minimal() +
  theme(axis.text.x=element_blank(), panel.grid.minor.y = element_blank()) +
  ggtitle("Excluding missing values") +
  ylim(-1,1)

### Without removing NA


plot2 <- ggplot() +
  geom_hline(yintercept=as.numeric(cor.test(PerHourNA[,Feature],PerHourNA$SFS)$estimate), linetype="dashed", color = "#0B3C69")  +
   geom_hline(yintercept=as.numeric(cor.test(PerDayNA[,Feature],PerDayNA$SFS)$estimate), linetype="dashed", color = "#708FF9") +
  geom_hline(yintercept=as.numeric(cor.test(PerWeekNA[,Feature],PerWeekNA$SFS)$estimate), linetype="dashed", color = "#FFCD3C") +
  geom_hline(yintercept=as.numeric(cor.test(PerStudyNA[,Feature],PerStudyNA$SFS)$estimate), linetype="dashed", color = "#FF5733") +
  ylab(element_blank()) +
  xlab("Participants") +
  scale_color_manual(name = "Resolution", values = c("Per Hour" = "#0B3C69", "Per Day" = "#708FF9", "Per Week" = "#FFCD3C")) +
  theme_minimal() +
  theme(axis.text.x=element_blank(), panel.grid.minor.y = element_blank()) +
  ggtitle("Including missing values") +
  ylim(-1,1)

plot <- ggarrange(plot1,plot2, common.legend = TRUE)

plot <- annotate_figure(plot, top = text_grob("Correlation:SFS)",color = "black", size = 14))

return(plot)
}
```

### Association Between Features
```{r echo=FALSE}
CorrelationPlot(Feature = c("HOME","COMMUNICATION"),PerHour,PerDay,PerWeek,PerStudy,PerHourNA,PerDayNA,PerWeekNA,PerStudyNA)
```
Maybe add to the plots the missing data number. Extreme effects on weeks: 1082,1242,1439. This are all participants in which a whole week of data is missing

HOME, COMMUNICATION


### Social Functioning Score

```{r echo=FALSE, warning=FALSE}
# Predict whether Alzheimer or Schizophrenia
## Random slopes
set.seed(12361488)

res_lin1 <- PerHour  %>% lm(SFS ~ HOME + UniqueNumber  + TotalMinutes + COMMUNICATION, data=.)

res_lin2 <- PerDay  %>% lm(SFS ~ HOME + UniqueNumber  + TotalMinutes + COMMUNICATION, data=.)

res_lin3 <- PerWeek  %>% lm(SFS ~ HOME + UniqueNumber  + TotalMinutes + COMMUNICATION, data=.)

res_lin4 <- PerStudy  %>% lm(SFS ~ HOME + UniqueNumber + TotalMinutes + COMMUNICATION, data=.)



plot2 <- dwplot(list(res_lin1,res_lin2,res_lin3), vline = geom_vline(
               xintercept = 0,
               colour = "grey60",
               linetype = 2
           )) +
 scale_colour_manual(name = "Resolution",labels = c("Per Week", "Per Day", "Per Hour"), values = c("#0B3C69","#708FF9", "#FFCD3C")) +
  theme_minimal() +
  ggtitle("\n Linear Regression")

plot2
```

## Predict to which class Participant belongs, differentiate between Alzheimer and Schizophrenia
### Missing data labeled as NA

```{r echo=FALSE, warning=FALSE}
# Predict whether Alzheimer or Schizophrenia
## Random slopes
set.seed(12361488)
res1 <- PerHour %>% filter(ParticipantLabel != "Label: 3 | Control") %>% glmer(as.factor(ParticipantLabel) ~  HOME + UniqueNumber + TotalMinutes + COMMUNICATION + (1 | ParticipantNumber), family=binomial, data=.)

coef1 <- coef(summary(res1)) %>%
    data.frame() %>%
    tibble::rownames_to_column("term") %>%
    rename(estimate = Estimate, std.error = Std..Error)

res2 <- PerDay  %>% filter(ParticipantLabel != "Label: 3 | Control") %>%  glmer(as.factor(ParticipantLabel) ~ HOME + UniqueNumber + TotalMinutes + COMMUNICATION + (1 | ParticipantNumber), family=binomial, data=.)

coef2 <- coef(summary(res2)) %>%
    data.frame() %>%
    tibble::rownames_to_column("term") %>%
    rename(estimate = Estimate, std.error = Std..Error)

res3 <- PerWeek  %>% filter(ParticipantLabel != "Label: 3 | Control") %>%  glmer(as.factor(ParticipantLabel) ~ HOME + UniqueNumber  + TotalMinutes + COMMUNICATION + (1 | ParticipantNumber), family=binomial, data=.)

coef3 <- coef(summary(res3)) %>%
    data.frame() %>%
    tibble::rownames_to_column("term") %>%
    rename(estimate = Estimate, std.error = Std..Error)

res4 <- PerStudy %>% filter(ParticipantLabel != "Label: 3 | Control") %>%  glm(as.factor(ParticipantLabel) ~ HOME + UniqueNumber  + TotalMinutes + COMMUNICATION, family=binomial, data=.)

coef1$model = "Per Hour"
coef2$model = "Per Day"
coef3$model = "Per Week"

plot1 <- dwplot(rbind(coef1,coef2,coef3), vline = geom_vline(
               xintercept = 0,
               colour = "grey60",
               linetype = 2
           )) +
  scale_colour_manual(name = "Resolution",labels = c("Per Week", "Per Day", "Per Hour"), values = c("#0B3C69","#708FF9", "#FFCD3C")) +
  theme_minimal() +
  ggtitle("Random Intercept \n Logistic Regression ")

### No random intercept
res_lin1 <- PerHour  %>% filter(ParticipantLabel != "Label: 3 | Control") %>%  glm(as.factor(ParticipantLabel) ~ HOME + UniqueNumber  + TotalMinutes + COMMUNICATION,family = "binomial", data=.)

res_lin2 <- PerDay  %>% filter(ParticipantLabel != "Label: 3 | Control") %>%  glm(as.factor(ParticipantLabel) ~ HOME + UniqueNumber  + TotalMinutes + COMMUNICATION,family = "binomial", data=.)

res_lin3 <- PerWeek  %>% filter(ParticipantLabel != "Label: 3 | Control") %>%  glm(as.factor(ParticipantLabel) ~ HOME + UniqueNumber  + TotalMinutes + COMMUNICATION,family = "binomial", data=.)

res_lin4 <- PerStudy  %>% filter(ParticipantLabel != "Label: 3 | Control") %>%  glm(as.factor(ParticipantLabel) ~ HOME + UniqueNumber + TotalMinutes + COMMUNICATION,family = "binomial", data=.)



plot2 <- dwplot(list(res_lin1,res_lin2,res_lin3), vline = geom_vline(
               xintercept = 0,
               colour = "grey60",
               linetype = 2
           )) +
 scale_colour_manual(name = "Resolution",labels = c("Per Week", "Per Day", "Per Hour"), values = c("#0B3C69","#708FF9", "#FFCD3C")) +
  theme_minimal() +
  ggtitle("\n Logistic Regression")

NAremove <- ggarrange(plot1 + theme(legend.position = "none"),plot2 + theme(axis.title.y=element_blank(),
           axis.text.y=element_blank(), 
           axis.ticks.y=element_blank()) , common.legend = FALSE)

NAremove <- annotate_figure(NAremove, top = text_grob("Differentiation between Alzheimer & Schizophrenia (Including Missing Values)",color = "black", size = 14))
NAremove
```

### Missing data labeled as 0

```{r echo=FALSE, warning=FALSE}
## Random slopes
res1NA <- PerHourNA  %>% filter(ParticipantLabel != "Label: 3 | Control") %>%  glmer(as.factor(ParticipantLabel) ~ HOME + UniqueNumber  + TotalMinutes + COMMUNICATION + (1 | ParticipantNumber), family=binomial, data=.)

coef1NA <- coef(summary(res1NA)) %>%
    data.frame() %>%
    tibble::rownames_to_column("term") %>%
    rename(estimate = Estimate, std.error = Std..Error)

res2NA <- PerDayNA  %>% filter(ParticipantLabel != "Label: 3 | Control") %>%  glmer(as.factor(ParticipantLabel) ~ HOME + UniqueNumber  + TotalMinutes + COMMUNICATION + (1 | ParticipantNumber), family=binomial, data=.)

coef2NA <- coef(summary(res2NA)) %>%
    data.frame() %>%
    tibble::rownames_to_column("term") %>%
    rename(estimate = Estimate, std.error = Std..Error)

res3NA <- PerWeekNA  %>% filter(ParticipantLabel != "Label: 3 | Control") %>%  glmer(as.factor(ParticipantLabel) ~ HOME + UniqueNumber  + TotalMinutes + COMMUNICATION + (1 | ParticipantNumber), family=binomial, data=.)

coef3NA <- coef(summary(res3NA)) %>%
    data.frame() %>%
    tibble::rownames_to_column("term") %>%
    rename(estimate = Estimate, std.error = Std..Error)

res4NA <- PerStudyNA %>% filter(ParticipantLabel != "Label: 3 | Control") %>%  glm(as.factor(ParticipantLabel) ~ HOME + UniqueNumber  + TotalMinutes + COMMUNICATION, family=binomial, data=.)

coef1NA$model = "Per Hour"
coef2NA$model = "Per Day"
coef3NA$model = "Per Week"

plot1NA <- dwplot(rbind(coef1NA,coef2NA,coef3NA), vline = geom_vline(
               xintercept = 0,
               colour = "grey60",
               linetype = 2
           )) +
  theme_minimal() +
  scale_colour_manual(name = "Resolution",labels = c("Per Week", "Per Day", "Per Hour"), values = c("#0B3C69","#708FF9", "#FFCD3C")) +
  ggtitle("Random Intercept \n Logistic Regression")


### No random slopes
res_lin1NA <- PerHourNA  %>% filter(ParticipantLabel != "Label: 3 | Control") %>%  glm(as.factor(ParticipantLabel) ~ HOME + UniqueNumber  + TotalMinutes + COMMUNICATION,family = "binomial", data=.)

res_lin2NA <- PerDayNA  %>% filter(ParticipantLabel != "Label: 3 | Control") %>%  glm(as.factor(ParticipantLabel) ~ HOME + UniqueNumber  + TotalMinutes + COMMUNICATION,family = "binomial", data=.)

res_lin3NA <- PerWeekNA  %>% filter(ParticipantLabel != "Label: 3 | Control") %>%  glm(as.factor(ParticipantLabel) ~ HOME + UniqueNumber  + TotalMinutes  + COMMUNICATION,family = "binomial", data=.)

res_lin4NA <- PerStudyNA  %>% filter(ParticipantLabel != "Label: 3 | Control") %>%  glm(as.factor(ParticipantLabel) ~ HOME + UniqueNumber  + TotalMinutes + COMMUNICATION,family = "binomial", data=.)



plot2NA <- dwplot(list(res_lin1NA,res_lin2NA,res_lin3NA), vline = geom_vline(
               xintercept = 0,
               colour = "grey60",
               linetype = 2
           )) +
  scale_colour_manual(name = "Resolution",labels = c("Per Week", "Per Day", "Per Hour"), values = c("#0B3C69","#708FF9", "#FFCD3C")) +
  theme_minimal() +
  ggtitle("\n Logistic Regression")

NAnotremove <- ggarrange(plot1NA + theme(legend.position = "none"),plot2NA + theme(axis.title.y=element_blank(),
           axis.text.y=element_blank(), 
           axis.ticks.y=element_blank()) , common.legend = FALSE)


NAnotremove <- annotate_figure(NAnotremove, top = text_grob("Differentiation between Alzheimer & Schizophrenia (Excluding Missing Values)",color = "black", size = 14))

NAnotremove
```

```{r echo=FALSE, warning=FALSE}
# combine plots NAremove & NAnotremove
stargazer(res1,res1NA,res_lin1,res_lin1NA,res2,res2NA,res_lin2,res_lin2NA,res3,res3NA,res_lin3,res_lin3NA, dep.var.labels.include	= F, type = "text", add.lines = list(c("Resolution", "Hour", "Hour", "Hour", "Hour","Day", "Day", "Day", "Day", "Week", "Week", "Week", "Week"),c("Missing Data excluded", "Yes", "No", "Yes", "No","Yes", "No", "Yes", "No","Yes", "No", "Yes", "No")))

stargazer(res1,res_lin1,res2,res_lin2,res3,res_lin3, dep.var.labels.include	= F, type = "text", add.lines =list( c("Resolution","Hour", "Hour", "Day", "Day", "Week", "Week")))

```

## Something with Change

```{r}
resultHour <- NULL
resultDay <- NULL
resultWeek <- NULL
resultStudy <- NULL

variables <- c("HOME",'HOME_moving24h', 'HOME_moving168h', 'HOME_moving8h','COMMUNICATION','TotalMinutes',"UniqueNumber")

for(i in 1:length(variables)){
resultHour[[i]] <- PerHour  %>% filter(ParticipantLabel != "Label: 4 | Schizophrenia") %>%  glm(as.formula(paste("as.factor(ParticipantLabel) ~", variables[i])),family = "binomial", data=.)
}

variables <- c("HOME",'HOME_moving7d', 'HOME_moving14d', 'HOME_moving28d','COMMUNICATION','TotalMinutes',"UniqueNumber")

for(i in 1:length(variables)){
resultDay[[i]] <- PerDay  %>% filter(ParticipantLabel != "Label: 4 | Schizophrenia") %>%  glm(as.formula(paste("as.factor(ParticipantLabel) ~", variables[i])) ,family = "binomial", data=.)
}

for(i in 1:length(variables)){
resultWeek[[i]] <- PerWeek  %>% filter(ParticipantLabel != "Label: 4 | Schizophrenia") %>%  glm(as.factor(ParticipantLabel) ~ HOME,family = "binomial", data=.)
}

for(i in 1:length(variables)){
resultStudy[[i]] <- PerStudy  %>% filter(ParticipantLabel != "Label: 4 | Schizophrenia") %>%  glm(as.factor(ParticipantLabel) ~ HOME,family = "binomial", data=.)
}

plot2 <- dwplot(c(resultHour,resultDay), vline = geom_vline(
               xintercept = 0,
               colour = "grey60",
               linetype = 2
           )) +
  theme_minimal() 

plot2
```


```{r}

```

