---
title: "Time_Scale_Paper"
author: "Anna Langener"
date: "4/22/2022"
output: word_document
---

```{r setup, include=FALSE}
library('dplyr')
library('ggplot2')
library('plotly')
library("runner")
library("hrbrthemes")
library("viridis")
library("ggpubr")
library("tidyr")
library("knitr")
library("dotwhisker")
library("stargazer")
library("lme4")


###### Scripts used ###########
# 0. Python script (Match with ESM data.ipynb)
# 1. data_matching.R
# 2. Calculation Correlation.R
# 3. ParallelComputingML.R

###### Load dataframes #########
################################

####### Affect data #######
#### Time interval used to label data as missing
#24h missing
Affect_Passive <- read.csv("/Users/annalangener/Nextcloud/BEHAPP data/FullDataset_2709_24missing.csv")
Affect_Passive <- Affect_Passive[Affect_Passive$questionListName != "Morning assessment 1" & Affect_Passive$questionListName != "Morning Assessment",]

#12h
Affect_Passive_12m <- read.csv("/Users/annalangener/Nextcloud/BEHAPP data/FullDataset_2709_12missing.csv")
Affect_Passive_12m <- Affect_Passive_12m[Affect_Passive_12m$questionListName != "Morning assessment 1" & Affect_Passive_12m$questionListName != "Morning Assessment",]

#18h
Affect_Passive_18m <- read.csv("/Users/annalangener/Nextcloud/BEHAPP data/FullDataset_2709_18missing.csv")
Affect_Passive_18m <- Affect_Passive_18m[Affect_Passive_18m$questionListName != "Morning assessment 1" & Affect_Passive_18m$questionListName != "Morning Assessment",]

### Label data as missing if any of the following sensors is not present;
# Apps (whole day without app usage)
# Location (whole day without GPS coordinates, based on raw GPS)
# Wifi (whole day without wifi data)
# Bluetooth (whole day without Bluetooth data)

Affect_Passive_allsensor_NA <- Affect_Passive
Affect_Passive_allsensor_NA_12m <- Affect_Passive_12m
Affect_Passive_allsensor_NA_18m <- Affect_Passive_18m

Affect_Passive_allsensor_NA[is.na(Affect_Passive$APP_USAGE_min) | is.na(Affect_Passive$TIME_STATIONARY_min) | is.na(Affect_Passive$TOTAL_MACHASHES_number) | is.na(Affect_Passive$BLUETOOTH_TOTAL_MACHASHES_number),!colnames(Affect_Passive_allsensor_NA) %in% c("ParticipantNumber","Date", "pa_mean", "na_mean", "timescale_beforeESM")] <- NA

Affect_Passive_allsensor_NA_12m[is.na(Affect_Passive_12m$APP_USAGE_min) | is.na(Affect_Passive_12m$TIME_STATIONARY_min) | is.na(Affect_Passive_12m$TOTAL_MACHASHES_number) | is.na(Affect_Passive_12m$BLUETOOTH_TOTAL_MACHASHES_number),!colnames(Affect_Passive_allsensor_NA_12m) %in% c("ParticipantNumber","Date", "pa_mean", "na_mean", "timescale_beforeESM")] <- NA

Affect_Passive_allsensor_NA_18m[is.na(Affect_Passive_18m$APP_USAGE_min) | is.na(Affect_Passive_18m$TIME_STATIONARY_min) | is.na(Affect_Passive_18m$TOTAL_MACHASHES_number) | is.na(Affect_Passive_18m$BLUETOOTH_TOTAL_MACHASHES_number),!colnames(Affect_Passive_allsensor_NA_18m) %in% c("ParticipantNumber","Date", "pa_mean", "na_mean", "timescale_beforeESM")] <- NA
```

### Temporal resolution while aggregating the data
#### Example 1.1: Descriptive Figures
```{r include=FALSE}
# load the grid library
library(grid)
# load the half_flat_violinplot.R file from the data repository
source("https://raw.githubusercontent.com/datavizpyr/data/master/half_flat_violinplot.R")

# order the timescale_beforeESM variable
Affect_Passive$timescale_beforeESM <- ordered(Affect_Passive$timescale_beforeESM,levels = c("1h","3h","6h","9h","12h","24h"))

# create a new variable timescale_beforeESM_num, which is a numeric version of timescale_beforeESM
Affect_Passive$timescale_beforeESM_num <- recode(Affect_Passive$timescale_beforeESM, "1h" = 1, "3h" = 3,"6h" = 6,"9h" = 9,"12h" = 12, "24h" = 24 )

####### GPS #######
###################
# create a plot of the GPS data for participant 117119
plot2 <-Affect_Passive[Affect_Passive$ParticipantNumber %in% c(117119),] %>%  ggplot(., aes( x = 1, y=Cluster_HOME_min/timescale_beforeESM_num/60, fill = timescale_beforeESM, color = timescale_beforeESM)) + 
  geom_flat_violin(alpha = 0.5, position = position_nudge(x = .3, y = 0), width = 0.6) +
  geom_point(position = position_jitter(seed = 1, width = 0.15, height = 0)) +
  theme_minimal() +
  xlab("") + 
  ylab("") +
  labs(fill='', color = '') +
  theme(legend.position = "none", axis.text.x=element_blank(),
        axis.ticks.x=element_blank(), text = element_text(size= 14), panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
  facet_grid(cols = vars(timescale_beforeESM)) +
  scale_color_manual(breaks = c("1h","3h","6h","9h","12h", "24h"),
                        values=c("#440154", "#443983", "#31688e","#21918c","#35b779","#90d743")) +
  scale_fill_manual(breaks = c("1h","3h","6h","9h","12h", "24h"),
                        values=c("#440154", "#443983", "#31688e","#21918c","#35b779","#90d743"))

# save the plot as a jpg file
ggsave(
  "plot_117119_simple.jpg",
  plot = plot2,
  width = 20,
  height = 6,
  units = c("cm"),
  dpi = 300,
  limitsize = TRUE,
  bg = NULL)



####### Calling #######
#######################

#### Add percentages for annotation
dat_text <- data.frame(label = c(mean(!Affect_Passive[Affect_Passive$ParticipantNumber %in% c(117130) & Affect_Passive$timescale_beforeESM == "1h" ,"CALL_TOTAL_min"]),mean(!Affect_Passive[Affect_Passive$ParticipantNumber %in% c(117130) & Affect_Passive$timescale_beforeESM == "3h" ,"CALL_TOTAL_min"]),mean(!Affect_Passive[Affect_Passive$ParticipantNumber %in% c(117130) & Affect_Passive$timescale_beforeESM == "6h" ,"CALL_TOTAL_min"]), mean(!Affect_Passive[Affect_Passive$ParticipantNumber %in% c(117130) & Affect_Passive$timescale_beforeESM == "9h" ,"CALL_TOTAL_min"]), mean(!Affect_Passive[Affect_Passive$ParticipantNumber %in% c(117130) & Affect_Passive$timescale_beforeESM == "12h" ,"CALL_TOTAL_min"]), mean(!Affect_Passive[Affect_Passive$ParticipantNumber %in% c(117130) & Affect_Passive$timescale_beforeESM == "24h" ,"CALL_TOTAL_min"])), timescale_beforeESM = c("1h","3h","6h","9h","12h", "24h"))
dat_text$label <- paste(round(dat_text$label*100),"%", sep = "")

dat_text$timescale_beforeESM <- factor(dat_text$timescale_beforeESM, ordered = TRUE, 
                                levels = c("1h","3h","6h","9h","12h", "24h"))

plot2 <-Affect_Passive[Affect_Passive$ParticipantNumber %in% c(117130),] %>%  ggplot(., aes( x = 1, y=CALL_TOTAL_min/timescale_beforeESM_num/60, fill = timescale_beforeESM, color = timescale_beforeESM)) + 
  geom_flat_violin(alpha = 0.5, position = position_nudge(x = .3, y = 0), width = 0.6) +
  geom_point(position = position_jitter(seed = 1, width = 0.15, height = 0)) +
  theme_minimal() +
  xlab("") + 
  ylab("") +
  labs(fill='', color = '') +
  theme(legend.position = "none", axis.text.x=element_blank(),
        axis.ticks.x=element_blank(), text = element_text(size= 14), panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
  geom_text(data    = dat_text,mapping = aes(x = -Inf, y = -Inf, label = label),x   = 1.47,y   = 0.03) +
#  geom_curve(data = dat_text, x = 1.45, y = 0.022, xend = 1.40, yend = 0, curvature = .1, arrow = arrow(length = unit(2, "mm"))) +
  facet_grid(cols = vars(timescale_beforeESM)) +
  scale_color_manual(breaks = c("1h","3h","6h","9h","12h", "24h"),
                        values=c("#440154", "#443983", "#31688e","#21918c","#35b779","#90d743")) +
  scale_fill_manual(breaks = c("1h","3h","6h","9h","12h", "24h"),
                        values=c("#440154", "#443983", "#31688e","#21918c","#35b779","#90d743"))

ggsave(
  "plot_117130_simple.jpg",
  plot = plot2,
  width = 20,
  height = 6,
  units = c("cm"),
  dpi = 300,
  limitsize = TRUE,
  bg = NULL)

```

Calculate mean value & standard deviation
```{r include=FALSE}
# this code is to calculate the mean and sd of the number of minutes spent at home per day
sum_stat_Home = Affect_Passive[Affect_Passive$ParticipantNumber %in% c(117119),] %>% group_by(timescale_beforeESM) %>% summarise(mean = mean(Cluster_HOME_min/timescale_beforeESM_num/60, na.rm = TRUE), sd = sd(Cluster_HOME_min/timescale_beforeESM_num/60, na.rm = TRUE))

# this code is to calculate the mean and sd of the number of calls per day
sum_stat_Call = Affect_Passive[Affect_Passive$ParticipantNumber %in% c(117130),] %>% group_by(timescale_beforeESM) %>% summarise(mean = mean(CALL_TOTAL_min/timescale_beforeESM_num, na.rm = TRUE), sd = sd(CALL_TOTAL_min/timescale_beforeESM_num, na.rm = TRUE))


```


#### Example 1.2: Correlation Analysis

```{r include=FALSE}
#Here we calculate the different Correlations
source("Calculation Correlation.R")

# Missing values labeled single sensor specific
CorrelationSampleTrue <- calculateCorr_pa(Affect_Passive)
CorrelationSampleTrue_18 <- calculateCorr_pa(Affect_Passive_18m)
CorrelationSampleTrue_12 <- calculateCorr_pa(Affect_Passive_12m)

# If one sensor is missing, all are missing
CorrelationSampleTrue_allNA <- calculateCorr_pa(Affect_Passive_allsensor_NA)
CorrelationSampleTrue_allNA_18 <- calculateCorr_pa(Affect_Passive_allsensor_NA_18m)
CorrelationSampleTrue_allNA_12 <- calculateCorr_pa(Affect_Passive_allsensor_NA_12m)

```

```{r include=FALSE}
### Correlation value
CorrelationSampleTrue[CorrelationSampleTrue$ParticipantNumber == 117119 & CorrelationSampleTrue$Feature == "Cluster_HOME_min",]

CorrelationSampleTrue[CorrelationSampleTrue$ParticipantNumber == 117130 & CorrelationSampleTrue$Feature == "CALL_TOTAL_min",] #Sensor specific?/ No exclusion
```

```{r include=FALSE}
### Calculate Sample size (sample size is the same for all measurements)
P117119 <- colSums(!is.na(Affect_Passive[Affect_Passive$ParticipantNumber == 117119 & Affect_Passive$timescale_beforeESM == "24h",]))
P117119["Cluster_HOME_min"]

P117130 <- colSums(!is.na(Affect_Passive[Affect_Passive$ParticipantNumber == 117130 & Affect_Passive$timescale_beforeESM == "24h",]))
P117130["CALL_TOTAL_min"]
```

Plots
```{r include=FALSE}
#Try out scatter plots
Home_scatter <- ggplot(Affect_Passive[Affect_Passive$ParticipantNumber %in% c(117119),], aes(x = Cluster_HOME_min, y = pa_mean )) +
  geom_point(colour = "#440154FF" ) +
  geom_smooth(method="lm", se=TRUE, fullrange=FALSE, level=0.95, colour ="#21908CFF", fill ="#21908CFF") +
  stat_cor(method = "pearson",p.accuracy = 0.01, r.accuracy = 0.01, label.y = 0.3, label.sep = ",", label.x = 0, na.rm = TRUE, cor.coef.name = c("r")) +
  theme_minimal() +
  facet_grid(cols = vars(timescale_beforeESM), scales="free_x") +
  ylim(c(0,10)) +
  ylab("Positive Affect") +
  xlab("Minutes being at Home")  +
theme(text = element_text(size= 16), axis.text.x=element_text(hjust = 0.8))

ggsave("plot_home_scatter.jpg",plot = Home_scatter, width = 26, height =8,units = c("cm"),dpi = 300,limitsize = FALSE,bg = NULL)

Phone_scatter <- ggplot(Affect_Passive[Affect_Passive$ParticipantNumber %in% c(117130),], aes(x = CALL_TOTAL_min, y = pa_mean )) +
  geom_point(colour = "#440154FF" ) +
  geom_smooth(method="lm", se=TRUE, fullrange=FALSE, level=0.95, colour ="#21908CFF", fill ="#21908CFF") +
  stat_cor(method = "pearson",p.accuracy = 0.01, r.accuracy = 0.01, label.y = 0.3, label.sep = ",", label.x = 0, na.rm = TRUE, cor.coef.name = c("r")) +
  theme_minimal() +
  facet_grid(cols = vars(timescale_beforeESM), scales="free_x") +
  ylim(c(0,10)) +
  ylab("Positive Affect") +
  xlab("Minutes of Calling")  +
theme(text = element_text(size= 16), axis.text.x=element_text(hjust = 0.8))

ggsave("plot_phone_scatter.jpg",plot = Phone_scatter, width = 26, height =8,units = c("cm"),dpi = 300,limitsize = FALSE,bg = NULL)

```


### Missing Data
#### Example 2: Using different missing data handling strategies to calculate the Correlation between Smartphone Measures and Affect
```{r include=FALSE}

### Function to calculate missing data ###
calculate_missingdata <- function(Affect_Passive){
Affect_Passive_subset_explore <- subset(Affect_Passive,
                                  select = c(ParticipantNumber, Date , na_mean , pa_mean , timescale_beforeESM,
                                              APP_USAGE_min ,
                                              TIME_STATIONARY_min ,
                                              TOTAL_MACHASHES_number ,
                                              BLUETOOTH_TOTAL_MACHASHES_number ,
                                              LIGHT_LUX_mean , 
                                              SCREEN_onLocked_number,
                                             CALL_TOTAL_min))


P117119 <- colSums(is.na(Affect_Passive_subset_explore[Affect_Passive_subset_explore$ParticipantNumber == 117119 & Affect_Passive_subset_explore$timescale_beforeESM == "9h",]))

P117130 <- colSums(is.na(Affect_Passive_subset_explore[Affect_Passive_subset_explore$ParticipantNumber == 117130 & Affect_Passive_subset_explore$timescale_beforeESM == "9h",]))

Overall <- colSums(is.na(Affect_Passive_subset_explore[Affect_Passive_subset_explore$timescale_beforeESM == "9h",]))
               
MissingValues <- cbind(P117119,P117130,Overall)

P117119_p <- round(colSums(is.na(Affect_Passive_subset_explore[Affect_Passive_subset_explore$ParticipantNumber == 117119 & Affect_Passive_subset_explore$timescale_beforeESM == "9h",]))/nrow(Affect_Passive_subset_explore[Affect_Passive_subset_explore$ParticipantNumber == 117119 & Affect_Passive_subset_explore$timescale_beforeESM == "9h",]),2)

P117130_p <- round(colSums(is.na(Affect_Passive_subset_explore[Affect_Passive_subset_explore$ParticipantNumber == 117130 & Affect_Passive_subset_explore$timescale_beforeESM == "9h",]))/nrow(Affect_Passive_subset_explore[Affect_Passive_subset_explore$ParticipantNumber == 117130 & Affect_Passive_subset_explore$timescale_beforeESM == "9h",]),2)

Overall_p <- round(colSums(is.na(Affect_Passive_subset_explore[Affect_Passive_subset_explore$timescale_beforeESM == "9h",]))/nrow(Affect_Passive_subset_explore[Affect_Passive_subset_explore$timescale_beforeESM == "9h",]),2)

MissingValues <- data.frame(cbind(MissingValues, P117119_p,P117130_p,Overall_p))
MissingValues$index <- rownames(MissingValues)

return(MissingValues)
}

### Calculate missing data

missing1 <- calculate_missingdata(Affect_Passive)
missing1 <- data.frame(missing1, cond = c(rep("Sensor Specific")), missing =  c(rep("Threshold: 24h")))

missing2 <- calculate_missingdata(Affect_Passive_allsensor_NA)
missing2 <- data.frame(missing2, cond = c(rep("Non Sensor Specific")), missing =  c(rep("Threshold: 24h")))

missing3 <- calculate_missingdata(Affect_Passive_18m)
missing3 <- data.frame(missing3, cond = c(rep("Sensor Specific")), missing =  c(rep("Threshold: 18h")))

missing4 <- calculate_missingdata(Affect_Passive_allsensor_NA_18m)
missing4 <- data.frame(missing4, cond = c(rep("Non Sensor Specific")), missing =  c(rep("Threshold: 18h")))

missing5 <- calculate_missingdata(Affect_Passive_12m)
missing5 <- data.frame(missing5, cond = c(rep("Sensor Specific")), missing =  c(rep("Threshold: 12h")))

missing6 <- calculate_missingdata(Affect_Passive_allsensor_NA_12m)
missing6 <- data.frame(missing6, cond = c(rep("Non Sensor Specific")), missing =  c(rep("Threshold: 12h")))

missing_plotdata <- rbind(missing1,missing2,missing3,missing4,missing5,missing6)

```

```{r include=FALSE}

plot_missing_gps <- ggplot(missing_plotdata[missing_plotdata$index == "TIME_STATIONARY_min",], aes(fill=cond, y=P117119_p, x=missing)) + 
    geom_bar(position="dodge", stat="identity") +
  theme_minimal() +
  scale_fill_manual(values = c("#440154", "#21918c"),breaks=c('Non Sensor Specific','Sensor Specific'),  labels = c("Excluded based on other measures","Only excluded if GPS is missing")) +
  theme( legend.title=element_blank()) +
  ggtitle("") +
  ylab("Proportions of excluded data") +
  xlab("") +
  #coord_cartesian(ylim=c(0,0.5)) +
  theme(legend.text = element_text(size=10), legend.position = "top") +
  geom_text(aes(label = paste("n =", round(P117119, 2))),position = position_dodge(0.8), vjust = -0.2)


ggsave(
  "plot_missingcount_poster.jpg",
  plot = plot_missing_gps,
  width = 14,
  height = 12,
  units = c("cm"),
  dpi = 300,
  limitsize = TRUE,
  bg = NULL)

```

### Moving Window
#### Example 3: Using a different level of aggregation and a different moving window to predict positive affect

```{r include=FALSE}
# set seed for reproducibility
set.seed(12361488)

# load required packages
library(caret)
library(forcats)

# read in the results of the machine learning models (for the supplementary material read the results from participant 117121)
OverallResults_1h <- read.csv("Results/OverallResults_1h.csv")
OverallResults_3h <- read.csv("Results/OverallResults_3h.csv")
OverallResults_6h <- read.csv("Results/OverallResults_6h.csv")
OverallResults_9h <- read.csv("Results/OverallResults_9h.csv")
OverallResults_12h <- read.csv("Results/OverallResults_12h.csv")
OverallResults_24h <- read.csv("Results/OverallResults_24h.csv")
MEAN_OverallResults <- read.csv("Results/OverallResults_MEAN.csv")



# function to calculate performance measures
perfromanceCalc <- function(OverallResults){
counter = 0
OverallResults <- OverallResults[OverallResults$index >= 43,]
for(i in unique(OverallResults$w)){
counter = counter + 1
results <- OverallResults[OverallResults$w == i,]

cor = cor.test(results$pred,results$true)$estimate
cor.int_1 = cor.test(results$pred,results$true)$conf.int[1]
cor.int_2 = cor.test(results$pred,results$true)$conf.int[2]
rss <- sum((results$pred - results$true) ^ 2)  ## residual sum of squares
tss <- sum((results$true - mean(results$true)) ^ 2)  ## total sum of squares
rsq <- 1 - rss/tss
RMSE <- RMSE(results$pred,results$true)

if(counter == 1){
resultsPerformance <- cbind(i,cor,cor.int_1,cor.int_2,rsq,RMSE)
OverallResultsPerformance <- resultsPerformance
}else{
resultsPerformance <- cbind(i,cor,cor.int_1,cor.int_2,rsq,RMSE)
OverallResultsPerformance <- rbind(OverallResultsPerformance, resultsPerformance)
}
OverallResultsPerformance <- as.data.frame(OverallResultsPerformance)
}
return(OverallResultsPerformance)
}

OverallResultsPerformance_1h <- perfromanceCalc(OverallResults_1h)
OverallResultsPerformance_3h <- perfromanceCalc(OverallResults_3h)
OverallResultsPerformance_6h <- perfromanceCalc(OverallResults_6h)
OverallResultsPerformance_9h <- perfromanceCalc(OverallResults_9h)
OverallResultsPerformance_12h <- perfromanceCalc(OverallResults_12h)
OverallResultsPerformance_24h <- perfromanceCalc(OverallResults_24h)

MEAN_OverallResultsPerformance <- perfromanceCalc(MEAN_OverallResults)

plot2 <- ggplot() +
   geom_line(aes(y = OverallResultsPerformance_24h$rsq, x = OverallResultsPerformance_24h$i, color = "24h")) +
  geom_line(aes(y = OverallResultsPerformance_12h$rsq, x = OverallResultsPerformance_12h$i, color = "12h")) +
  geom_line(aes(y = OverallResultsPerformance_9h$rsq, x = OverallResultsPerformance_9h$i, color = "9h")) +
    geom_line(aes(y = OverallResultsPerformance_6h$rsq, x = OverallResultsPerformance_6h$i, color = "6h")) +
     geom_line(aes(y = OverallResultsPerformance_3h$rsq, x = OverallResultsPerformance_3h$i, color = "3h")) +
     geom_line(aes(y = OverallResultsPerformance_1h$rsq, x = OverallResultsPerformance_1h$i, color = "1h")) +
      geom_line(aes(y = MEAN_OverallResultsPerformance$rsq, x = MEAN_OverallResultsPerformance$i, color = "rolling mean"), size = 1.3) +
  theme_minimal() +
  xlab("Number of observations used for building the prediction model") +
  ylab("R-squared") +
 scale_color_viridis(discrete=TRUE,limits = c("24h","12h","9h","6h","3h","1h","rolling mean")) +
  labs(color = "Level of Aggregation")  +
    # Annotation
  annotate(
    geom = "curve", x = 12, y = 0.165, xend = 11, yend = 0.070, 
    curvature = .2,  colour = "#909090", arrow = arrow(length = unit(2, "mm"))
  ) +
  annotate(geom = "text", colour = "#838383", x = 6.1, y = 0.04, label = "Data aggregated one hour before ESM \noverall leads to worse predictions \ncompared to broader time scales.", hjust = "left") +
   annotate(
    geom = "curve", colour = "#909090", x = 35, y = 0.065, xend = 28, yend = 0.029, 
    curvature = .2, arrow = arrow(length = unit(2, "mm"))
  ) +
  annotate(geom = "text", colour = "#838383", x = 22, y = 0.01, label = "The prediction accuracy further decreases \nfor choosing larger moving window sizes.", hjust = "left") +
  theme(legend.text = element_text(size=11))


 ggsave(
 "RSquared.jpg",
 plot = plot2,
 width = 23,
 height = 10,
 units = c("cm"),
 dpi = 300,
 limitsize = TRUE,
 bg = NULL)

```

Paper report Rsquared and confidence
```{r include=FALSE}
#### Level of Aggregation

#Correlation 1h
max <- which(OverallResultsPerformance_1h$rsq == max(OverallResultsPerformance_1h$rsq))
min <- which(OverallResultsPerformance_1h$rsq == min(OverallResultsPerformance_1h$rsq))

paste("(m = ",round(mean(OverallResultsPerformance_1h$rsq),2), ", max = ",round(OverallResultsPerformance_1h$rsq[max],2),", min = ",round(OverallResultsPerformance_1h$rsq[min],2),")", sep = "")

#Correlation 3h
max <- which(OverallResultsPerformance_3h$rsq == max(OverallResultsPerformance_3h$rsq))
min <- which(OverallResultsPerformance_3h$rsq == min(OverallResultsPerformance_3h$rsq))

paste("(m = ",round(mean(OverallResultsPerformance_3h$rsq),2), ", max = ",round(OverallResultsPerformance_3h$rsq[max],2),", min = ",round(OverallResultsPerformance_3h$rsq[min],2),")", sep = "")

#Correlation 6h
max <- which(OverallResultsPerformance_6h$cor == max(OverallResultsPerformance_6h$cor))
min <- which(OverallResultsPerformance_6h$cor == min(OverallResultsPerformance_6h$cor))

paste("(m = ",round(mean(OverallResultsPerformance_6h$rsq),2), ", max = ",round(OverallResultsPerformance_6h$rsq[max],2),", min = ",round(OverallResultsPerformance_6h$rsq[min],2),")", sep = "")

#Correlation 9h
max <- which(OverallResultsPerformance_9h$rsq == max(OverallResultsPerformance_9h$rsq))
min <- which(OverallResultsPerformance_9h$rsq == min(OverallResultsPerformance_9h$rsq))

paste("(m = ",round(mean(OverallResultsPerformance_9h$rsq),2), ", max = ",round(OverallResultsPerformance_9h$rsq[max],2),", min = ",round(OverallResultsPerformance_9h$rsq[min],2),")", sep = "")

#Correlation 12h
max <- which(OverallResultsPerformance_12h$rsq == max(OverallResultsPerformance_12h$rsq))
min <- which(OverallResultsPerformance_12h$rsq == min(OverallResultsPerformance_12h$rsq))


paste("(m = ",round(mean(OverallResultsPerformance_12h$rsq),2), ", max = ",round(OverallResultsPerformance_12h$rsq[max],2),", min = ",round(OverallResultsPerformance_12h$rsq[min],2),")", sep = "")

#Correlation 24h
max <- which(OverallResultsPerformance_24h$rsq == max(OverallResultsPerformance_24h$rsq))
min <- which(OverallResultsPerformance_24h$rsq == min(OverallResultsPerformance_24h$rsq))

paste("(m = ",round(mean(OverallResultsPerformance_24h$rsq),2), ", max = ",round(OverallResultsPerformance_24h$rsq[max],2),", min = ",round(OverallResultsPerformance_24h$rsq[min],2),")", sep = "")


#### Moving Window
##1h
#Lowest window
paste("(R-Squared = ",round(OverallResultsPerformance_1h$rsq[1],2),")", sep = "")

#highest window
paste("(R-Squared = ",round(OverallResultsPerformance_1h$rsq[37],2),")", sep = "")

##24h
#Lowest window
paste("(R-Squared = ",round(OverallResultsPerformance_24h$rsq[1],2),")", sep = "")

#highest window
paste("(R-Squared = ",round(OverallResultsPerformance_24h$rsq[37],2),")", sep = "")

```

### Supplementary Material - Other Sensors and Participants
```{r echo=FALSE}
source("Calculation Correlation.R")
#CorrelationSampleTrue <- calculateCorr_pa(Affect_Passive)

Variables <- unique(CorrelationSampleTrue$Feature)

for(i in 1:length(Variables)){
cor1 =  ggplot(CorrelationSampleTrue[CorrelationSampleTrue$Feature == Variables[i], ],
                     aes(
                       y = as.factor(ParticipantNumber),
                       x = as.factor(timescale_beforeESM),
                       fill = Correlation
                     )) +
        geom_tile() +
        scale_fill_gradient2(low = "#D7191C", mid = "white", high = "#2C7BB6", limits =  c(-0.5,0.5)) +
        geom_text(aes(label = star), color = "black", size = 4) +
        ylab("") +
        xlab("") +
        ggtitle(paste("Correlation between Positive Affect &", paste(Variables[i]))) +
        theme_minimal() +
    theme(plot.title = element_text(size = 9))
print(cor1)
}
```
