---
title: "Time_Scale_Paper"
author: "Anna Langener"
date: "4/22/2022"
output: 
    rmarkdown::html_document:
runtime: shiny
---

```{r setup, include=FALSE}
library('dplyr')
library('ggplot2')
library('plotly')
library("runner")
library("hrbrthemes")
library("viridis")
library("ggpubr")
library("tidyr")
library("knitr")
library("dotwhisker")
library("stargazer")
library("lme4")

###### Load dataframes #########
################################

#Between old and new dataset there might be small differences for 24h because sometimes the day was in the raw data even if nothing was recorded (for bluetooth, the rest should be similar) (example 117130)

####### Affect data #######
#Affect_Passive <- read.csv("/Users/annalangener/Nextcloud/BEHAPP data/FullDataset_220422")

#24h missing
Affect_Passive <- read.csv("/Users/annalangener/Nextcloud/BEHAPP data/FullDataset_090622_24missing.csv")
Affect_Passive <- Affect_Passive[Affect_Passive$questionListName != "Morning assessment 1" & Affect_Passive$questionListName != "Morning Assessment",]

#12h
Affect_Passive_12m <- read.csv("/Users/annalangener/Nextcloud/BEHAPP data/FullDataset_090622_12missing.csv")
Affect_Passive_12m <- Affect_Passive_12m[Affect_Passive_12m$questionListName != "Morning assessment 1" & Affect_Passive_12m$questionListName != "Morning Assessment",]

#18h
Affect_Passive_18m <- read.csv("/Users/annalangener/Nextcloud/BEHAPP data/FullDataset_090622_18missing.csv")
Affect_Passive_18m <- Affect_Passive_18m[Affect_Passive_18m$questionListName != "Morning assessment 1" & Affect_Passive_18m$questionListName != "Morning Assessment",]

### Labeled following sensors as missing:
# Apps (whole day without app usage)
# Location (whole day without GPS coordinates, based on raw GPS)
# Wifi (whole day without wifi data)
# Bluetooth (whole day without Bluetooth data)

Affect_Passive_allsensor_NA <- Affect_Passive
Affect_Passive_allsensor_NA_12m <- Affect_Passive_12m
Affect_Passive_allsensor_NA_18m <- Affect_Passive_18m

Affect_Passive_allsensor_NA[is.na(Affect_Passive$APP_USAGE_min) | is.na(Affect_Passive$TIME_STATIONARY_min) | is.na(Affect_Passive$TOTAL_MACHASHES_number) | is.na(Affect_Passive$BLUETOOTH_TOTAL_MACHASHES_number),!colnames(Affect_Passive_allsensor_NA) %in% c("ParticipantNumber","Date", "pa_mean", "na_mean", "timescale_beforeESM")] <- NA

Affect_Passive_allsensor_NA_12m[is.na(Affect_Passive_12m$APP_USAGE_min) | is.na(Affect_Passive_12m$TIME_STATIONARY_min) | is.na(Affect_Passive_12m$TOTAL_MACHASHES_number) | is.na(Affect_Passive_12m$BLUETOOTH_TOTAL_MACHASHES_number),!colnames(Affect_Passive_allsensor_NA_12m) %in% c("ParticipantNumber","Date", "pa_mean", "na_mean", "timescale_beforeESM")] <- NA

Affect_Passive_allsensor_NA_18m[is.na(Affect_Passive_18m$APP_USAGE_min) | is.na(Affect_Passive_18m$TIME_STATIONARY_min) | is.na(Affect_Passive_18m$TOTAL_MACHASHES_number) | is.na(Affect_Passive_18m$BLUETOOTH_TOTAL_MACHASHES_number),!colnames(Affect_Passive_allsensor_NA_18m) %in% c("ParticipantNumber","Date", "pa_mean", "na_mean", "timescale_beforeESM")] <- NA

Affect_Passive_no_NA <- Affect_Passive

Affect_Passive_no_NA[is.na(Affect_Passive_no_NA)] <- 0

```

Missing data
```{r eval=FALSE, include=FALSE}

calculate_missingdata <- function(Affect_Passive){
Affect_Passive_subset_explore <- subset(Affect_Passive,
                                  select = c(ParticipantNumber, Date , na_mean , pa_mean , timescale_beforeESM,
                                              APP_USAGE_min ,
                                              TIME_STATIONARY_min ,
                                              TOTAL_MACHASHES_number ,
                                              BLUETOOTH_TOTAL_MACHASHES_number ,
                                              LIGHT_LUX_mean , 
                                              SCREEN_onLocked_number,
                                             CALL_TOTAL_min))


P117119 <- colSums(is.na(Affect_Passive_subset_explore[Affect_Passive_subset_explore$ParticipantNumber == 117119 & Affect_Passive_subset_explore$timescale_beforeESM == "9h",]))

P117130 <- colSums(is.na(Affect_Passive_subset_explore[Affect_Passive_subset_explore$ParticipantNumber == 117130 & Affect_Passive_subset_explore$timescale_beforeESM == "9h",]))

Overall <- colSums(is.na(Affect_Passive_subset_explore[Affect_Passive_subset_explore$timescale_beforeESM == "9h",]))
               
MissingValues <- cbind(P117119,P117130,Overall)


P117119_p <- round(colSums(is.na(Affect_Passive_subset_explore[Affect_Passive_subset_explore$ParticipantNumber == 117119 & Affect_Passive_subset_explore$timescale_beforeESM == "9h",]))/nrow(Affect_Passive_subset_explore[Affect_Passive_subset_explore$ParticipantNumber == 117119 & Affect_Passive_subset_explore$timescale_beforeESM == "9h",]),2)


P117130_p <- round(colSums(is.na(Affect_Passive_subset_explore[Affect_Passive_subset_explore$ParticipantNumber == 117130 & Affect_Passive_subset_explore$timescale_beforeESM == "9h",]))/nrow(Affect_Passive_subset_explore[Affect_Passive_subset_explore$ParticipantNumber == 117130 & Affect_Passive_subset_explore$timescale_beforeESM == "9h",]),2)


Overall_p <- round(colSums(is.na(Affect_Passive_subset_explore[Affect_Passive_subset_explore$timescale_beforeESM == "9h",]))/nrow(Affect_Passive_subset_explore[Affect_Passive_subset_explore$timescale_beforeESM == "9h",]),2)


MissingValues <- data.frame(cbind(MissingValues, P117119_p,P117130_p,Overall_p))
MissingValues$index <- rownames(MissingValues)

return(MissingValues)
}

missing1 <- calculate_missingdata(Affect_Passive)
missing1 <- data.frame(missing1, cond = c(rep("Sensor Specific")), missing =  c(rep("Exclude: 24h")))

missing2 <- calculate_missingdata(Affect_Passive_allsensor_NA)
missing2 <- data.frame(missing2, cond = c(rep("Non Sensor Specific")), missing =  c(rep("Exclude: 24h")))

missing3 <- calculate_missingdata(Affect_Passive_18m)
missing3 <- data.frame(missing3, cond = c(rep("Sensor Specific")), missing =  c(rep("Exclude: 18h")))

missing4 <- calculate_missingdata(Affect_Passive_allsensor_NA_18m)
missing4 <- data.frame(missing4, cond = c(rep("Non Sensor Specific")), missing =  c(rep("Exclude: 18h")))

missing5 <- calculate_missingdata(Affect_Passive_12m)
missing5 <- data.frame(missing5, cond = c(rep("Sensor Specific")), missing =  c(rep("Exclude: 12h")))

missing6 <- calculate_missingdata(Affect_Passive_allsensor_NA_12m)
missing6 <- data.frame(missing6, cond = c(rep("Non Sensor Specific")), missing =  c(rep("Exclude: 12h")))

missing_plotdata <- rbind(missing1,missing2,missing3,missing4,missing5,missing6)
```

```{r eval=FALSE, include=FALSE}
missing_plotdata <- missing_plotdata
plot_missing_gps <- ggplot(missing_plotdata[missing_plotdata$index == "TIME_STATIONARY_min",], aes(fill=cond, y=P117119_p, x=missing)) + 
    geom_bar(position="dodge", stat="identity") +
  theme_minimal() +
  scale_fill_manual(values = c("#21918c","#440154"),breaks=c('Sensor Specific', 'Non Sensor Specific'),  labels = c("One measure excluded", "All measures excluded")) +
  theme( legend.title=element_blank()) +
  ggtitle("Exclusion GPS Data (Participant A)") +
  ylab("Percentage of excluded Data") +
  xlab("") +
  coord_cartesian(ylim=c(0,0.5)) +
  theme(legend.text = element_text(size=10)) 

plot_missing_gps_poster <- ggplot(missing_plotdata[missing_plotdata$index == "TIME_STATIONARY_min",], aes(fill=cond, y=P117119_p, x=missing)) + 
    geom_bar(position="dodge", stat="identity") +
  theme_minimal() +
  scale_fill_manual(values = c("#21918c","#440154"),breaks=c('Sensor Specific', 'Non Sensor Specific'),  labels = c("One measure excluded", "All measures excluded")) +
  theme( legend.title=element_blank()) +
  ggtitle("% of excluded GPS Data using different Strategies") +
  ylab("Percentage of excluded Data") +
  xlab("") +
#  coord_cartesian(ylim=c(0,0.5)) +
  theme(legend.text = element_text(size=14),legend.position="bottom", axis.text = element_text(size = 14),axis.title=element_text(size=16), plot.title = element_text(size=18)) 
ggsave(
  "plot_missingcount_poster.jpg",
  plot = plot_missing_gps_poster,
  width = 16,
  height = 14,
  units = c("cm"),
  dpi = 300,
  limitsize = TRUE,
  bg = NULL)

plot_missing_call <- ggplot(missing_plotdata[missing_plotdata$index == "CALL_TOTAL_min",], aes(fill=cond, y=P117130_p, x=missing)) + 
    geom_bar(position="dodge", stat="identity") +
  theme_minimal() +
  scale_fill_manual(values = c("#21918c","#440154"),breaks=c('Sensor Specific', 'Non Sensor Specific'),labels = c("One measure excluded", "All measures excluded")) +
  theme( legend.title=element_blank()) +
  ggtitle("Exclusion Call Data (Participant B)") +
  ylab("Percentage of excluded Data") +
  xlab("") +
  coord_cartesian(ylim=c(0,0.5)) +
  theme(legend.text = element_text(size=10)) 

plot_missingcount <- ggarrange(plot_missing_gps,plot_missing_call, common.legend =  TRUE, legend = "right")

plot_missingcount

ggsave(
  "plot_missingcount.jpg",
  plot = plot_missingcount,
  width = 25,
  height = 13,
  units = c("cm"),
  dpi = 300,
  limitsize = TRUE,
  bg = NULL)

```

### Plot for SAA
```{r eval=FALSE, include=FALSE}
missing_plotdata <- missing_plotdata[missing_plotdata$cond == "Sensor Specific", ]
plot_missing_gps <- ggplot(missing_plotdata[missing_plotdata$index == "TIME_STATIONARY_min",], aes(fill=cond, y=P117119_p, x=missing)) + 
    geom_bar(position="dodge", stat="identity") +
  theme_minimal() +
  scale_fill_manual(values = c("#21918c") ,breaks=c('Sensor Specific')) +
  theme( legend.title=element_blank()) +
  ggtitle("Exclusion GPS Data") +
  ylab("Percentage of excluded Data") +
  xlab("") +
  coord_cartesian(ylim=c(0,0.5)) +
  theme(legend.text = element_text(size=10)) 

plot_missing_gps_poster <- ggplot(missing_plotdata[missing_plotdata$index == "TIME_STATIONARY_min",], aes(fill=cond, y=P117119_p, x=missing)) + 
    geom_bar(position="dodge", stat="identity") +
  theme_minimal() +
  scale_fill_manual(values = c("#21918c","#440154"),breaks=c('Sensor Specific', 'Non Sensor Specific')) +
  theme( legend.title=element_blank()) +
  ggtitle("% of excluded GPS Data using different Strategies") +
  ylab("Percentage of excluded Data") +
  xlab("") +
#  coord_cartesian(ylim=c(0,0.5)) +
  theme(legend.text = element_text(size=14),legend.position="bottom", axis.text = element_text(size = 14),axis.title=element_text(size=16), plot.title = element_text(size=18)) 
  
ggsave(
  "plot_missingcount_SAA.jpg",
  plot = plot_missing_gps,
  width = 16,
  height = 14,
  units = c("cm"),
  dpi = 300,
  limitsize = TRUE,
  bg = NULL)

plot_missing_call <- ggplot(missing_plotdata[missing_plotdata$index == "CALL_TOTAL_min",], aes(fill=cond, y=P117130_p, x=missing)) + 
    geom_bar(position="dodge", stat="identity") +
  theme_minimal() +
  scale_fill_manual(values = c("#21918c","#440154"),breaks=c('Sensor Specific', 'Non Sensor Specific')) +
  theme( legend.title=element_blank()) +
  ggtitle("Exclusion Call Data (Participant B)") +
  ylab("Percentage of excluded Data") +
  xlab("") +
  coord_cartesian(ylim=c(0,0.5)) +
  theme(legend.text = element_text(size=10)) 

plot_missingcount <- ggarrange(plot_missing_gps,plot_missing_call, common.legend =  TRUE, legend = "right")

plot_missingcount

ggsave(
  "plot_missingcount.jpg",
  plot = plot_missingcount,
  width = 25,
  height = 13,
  units = c("cm"),
  dpi = 300,
  limitsize = TRUE,
  bg = NULL)

```




#Plot Missing Data (for Poster)
```{r eval=FALSE, include=FALSE}
Affect_Passive_sube <- Affect_Passive[Affect_Passive$ParticipantNumber %in% c(117119) & Affect_Passive$timescale_beforeESM == "24h",]
Affect_Passive_sube <- Affect_Passive_sube[1:52,]

plota <- ggplot(Affect_Passive_sube) +
  geom_line(aes(y = APP_USAGE_min, x = as.POSIXct(Date),color = "App Usage")) +
  geom_line(aes(y = TOTAL_MACHASHES_number/20, x = as.POSIXct(Date),color = "Total Wifi Connections")) +
  theme_minimal() +
  xlab("") + 
  ylab("") +
  labs(color='') +
  scale_y_continuous(
              name = "App Usage",
              sec.axis = sec_axis( ~ . * 20, name = 'Wifi Connections')
            ) +
  ggtitle("a) Only the missing measure is excluded") +
  scale_color_manual(name = "",values = c( "App Usage" = "#21918c", "Total Wifi Connections" = "#440154")) +
  annotate(
    geom = "curve", x = as.POSIXct(Affect_Passive_sube$Date[40]), y = 11, xend =as.POSIXct(Affect_Passive_sube$Date[35]), yend = 9, 
    curvature = .3, arrow = arrow(length = unit(2, "mm"))
  ) +
  annotate(geom = "text", x = as.POSIXct(Affect_Passive_sube$Date[40]), y = 11, label = "App Usage included,\n Wifi excluded", hjust = "left") +
  theme(legend.text = element_text(size=12))


Affect_Passive_sube <- Affect_Passive_allsensor_NA[Affect_Passive_allsensor_NA$ParticipantNumber %in% c(117119) & Affect_Passive_allsensor_NA$timescale_beforeESM == "24h",]
Affect_Passive_sube <- Affect_Passive_sube[1:50,]

plotb <- ggplot(Affect_Passive_sube) +
  geom_line(aes(y = APP_USAGE_min, x = as.POSIXct(Date),color = "App Usage")) +
  geom_line(aes(y = TOTAL_MACHASHES_number/20, x = as.POSIXct(Date),color = "Total Wifi Connections")) +
  theme_minimal() +
  xlab("") + 
  ylab("") +
  labs(color='') +
  scale_y_continuous(
              name = "App Usage",
              sec.axis = sec_axis( ~ . * 20, name = 'Wifi Connections')
            ) +
  ggtitle("b) All measures are excluded, if one measure is missing") +
  scale_color_manual(name = "",values = c( "App Usage" = "#21918c", "Total Wifi Connections" = "#440154")) +
  annotate(
    geom = "curve", x = as.POSIXct(Affect_Passive_sube$Date[40]), y = 11, xend =as.POSIXct(Affect_Passive_sube$Date[35]), yend = 9, 
    curvature = .3, arrow = arrow(length = unit(2, "mm"))
  ) +
  annotate(geom = "text", x = as.POSIXct(Affect_Passive_sube$Date[40]), y = 11, label = "Both measures \n excluded", hjust = "left") +
  theme(legend.text = element_text(size=12))


plot_exclusion <- ggarrange(plota, plotb, ncol = 1, common.legend = TRUE, legend = "bottom") 

ggsave(
  "plotexclude.jpg",
  plot = plot_exclusion,
  width = 17,
  height = 13,
  units = c("cm"),
  dpi = 300,
  limitsize = TRUE,
  bg = NULL)

```

### Plot Missing data (only to explore not for paper)
```{r eval=FALSE, include=FALSE}
Affect_Passive_sube <- Affect_Passive[Affect_Passive$ParticipantNumber %in% c(117130) & Affect_Passive$timescale_beforeESM == "24h",]
Affect_Passive_sube <- Affect_Passive_sube[1:50,]

#117130
Affect_Passive_allsensor_NA

plota <- ggplot() +
  geom_line(aes(y = Affect_Passive_allsensor_NA$Cluster_HOME_min[Affect_Passive_allsensor_NA$ParticipantNumber %in% c(117119) & Affect_Passive_allsensor_NA$timescale_beforeESM == "24h"], x = as.POSIXct(Affect_Passive_allsensor_NA$Date[Affect_Passive_allsensor_NA$ParticipantNumber %in% c(117119) & Affect_Passive_allsensor_NA$timescale_beforeESM == "24h"]),color = "24 hour")) +
   geom_line(aes(y = Affect_Passive_allsensor_NA_18m$Cluster_HOME_min[Affect_Passive_allsensor_NA_18m$ParticipantNumber %in% c(117119) & Affect_Passive_allsensor_NA_18m$timescale_beforeESM == "24h"], x = as.POSIXct(Affect_Passive_allsensor_NA_18m$Date[Affect_Passive_allsensor_NA_18m$ParticipantNumber %in% c(117119) & Affect_Passive_allsensor_NA_18m$timescale_beforeESM == "24h"]),color = "18 hour")) +
  geom_line(aes(y = Affect_Passive_allsensor_NA_12m$Cluster_HOME_min[Affect_Passive_allsensor_NA_12m$ParticipantNumber %in% c(117119) & Affect_Passive_allsensor_NA_12m$timescale_beforeESM == "24h"], x = as.POSIXct(Affect_Passive_allsensor_NA_12m$Date[Affect_Passive_allsensor_NA_12m$ParticipantNumber %in% c(117119) & Affect_Passive_allsensor_NA_12m$timescale_beforeESM == "24h"]),color = "12 hour")) +
  theme_minimal() +
  xlab("") + 
  ylab("")


```

### VISUALIZATION
In this example we test whether the level of aggregation matters

#### Affect & Passive Measure (CHANGE DESCREPTIVE PLOTS)


Descriptive Plots

```{r eval=FALSE, include=FALSE}
library(grid)
source("https://raw.githubusercontent.com/datavizpyr/data/master/half_flat_violinplot.R")

plot_data <- function(Affect_Passive){
Affect_Passive$timescale_beforeESM <- ordered(Affect_Passive$timescale_beforeESM,levels = c("1h","3h","6h","9h","12h","24h"))

Affect_Passive$timescale_beforeESM_num <- recode(Affect_Passive$timescale_beforeESM, "1h" = 1, "3h" = 3,"6h" = 6,"9h" = 9,"12h" = 12, "24h" = 24 )

#117110 Being at Home
plot1 <- ggplot(Affect_Passive[Affect_Passive$ParticipantNumber %in% c(117119),],aes(colour = factor(timescale_beforeESM))) +
  geom_line(aes(y = Cluster_HOME_min/timescale_beforeESM_num/60, x = as.POSIXct(Date))) +
  scale_x_datetime(date_labels = '%d-%m',breaks='1 weeks') +
#  theme_minimal() +
  xlab("") + 
  ylab("") +
  labs(color='') +
  ggtitle("Being at Home Total Minutes (in Percentage)") +
  facet_grid(cols = vars(timescale_beforeESM)) +
  theme(axis.text.x = element_text(angle = 45),legend.key = element_blank(),panel.background  = element_blank(), panel.grid = element_line(colour = "black"), panel.grid.major = element_line(size = rel(0.1)), panel.grid.minor = element_line(size = rel(0.05)) ) 


plot2 <- ggplot(Affect_Passive[Affect_Passive$ParticipantNumber %in% c(117119),], aes(x=timescale_beforeESM, y=Cluster_HOME_min/timescale_beforeESM_num/60, fill = timescale_beforeESM, color = timescale_beforeESM)) + 
  geom_flat_violin(alpha = 0.5, position = position_nudge(x = .3, y = 0)) +
  geom_point(position = position_jitter(seed = 1, width = 0.15)) +
  theme_minimal() +
  xlab("") + 
  ylab("") +
  labs(fill='', color = '') +
  theme(
  axis.text.x = element_blank(),
  axis.ticks = element_blank())


plot_117119 <- ggarrange(plot1, plot2, ncol = 1, common.legend = TRUE, legend = "right")
return(plot_117119)
}

ggsave(
  "plot_117119_2.jpg",
  plot = plot_117119,
  width = 20,
  height = 10,
  units = c("cm"),
  dpi = 300,
  limitsize = TRUE,
  bg = NULL)

#117130 Minutes of Calling
plot1 <- ggplot(Affect_Passive[Affect_Passive$ParticipantNumber %in% c(117130),],aes(colour = factor(timescale_beforeESM))) +
  geom_line(aes(y = CALL_TOTAL_min/timescale_beforeESM_num/60, x = as.POSIXct(Date))) +
  scale_x_datetime(date_labels = '%d-%m',breaks='1 weeks') +
#  theme_minimal() +
  xlab("") + 
  ylab("") +
  labs(color='') +
  ggtitle("Call Total Minutes (in Percentage)") +
  facet_grid(cols = vars(timescale_beforeESM)) +
  theme(axis.text.x = element_text(angle = 45),legend.key = element_blank(),panel.background  = element_blank(), panel.grid = element_line(colour = "black"), panel.grid.major = element_line(size = rel(0.1)), panel.grid.minor = element_line(size = rel(0.05)) ) 

plot2 <- ggplot(Affect_Passive[Affect_Passive$ParticipantNumber %in% c(117130),], aes(x=timescale_beforeESM, y=CALL_TOTAL_min/timescale_beforeESM_num/60, fill = timescale_beforeESM, color = timescale_beforeESM)) + 
  geom_flat_violin(alpha = 0.5, position = position_nudge(x = .3, y = 0)) +
  geom_point(position = position_jitter(seed = 1, width = 0.15)) +
  theme_minimal() +
  xlab("") + 
  ylab("") +
  labs(fill='', color = '') +
  theme(
  axis.text.x = element_blank(),
  axis.ticks = element_blank())


plot_117130 <- ggarrange(plot1, plot2, ncol = 1, common.legend = TRUE, legend = "right") 

ggsave(
  "plot_117130_2.jpg",
  plot = plot_117130,
  width = 20,
  height = 10,
  units = c("cm"),
  dpi = 300,
  limitsize = TRUE,
  bg = NULL)

```

Descriptive Figure as shiny app:

```{r echo=FALSE}

shinyApp(
  ui = fluidPage(
    selectInput(
      "Participant",
      label = "Participant: ",
      choices = c(117113,117114,117119,117121,117130,117129,117131,117134,117135,117137),
      selected = 117119
    ),
       selectInput(
      "PassiveMeasure",
      label = "Passive Measure: ",
       choices = c(
          'SOCIAL_min',
           'COMMUNICATION_min',
           'APP_USAGE_min',
           'APPS_OPENED_number',
           'Cluster_HOME_min',
           "Cluster_1_min",
           "Cluster_2_min",
           "Cluster_3_min",
           "Cluster_4_min",
           "Cluster_5_min" ,
           'UNIQUE_STAYPOINTS_number',
           'TIME_STATIONARY_min',
           'TOTAL_MACHASHES_number',
           'UNIQUE_MACHASHES_number',
           "BLUETOOTH_TOTAL_MACHASHES_number",
           "BLUETOOTH_UNIQUE_MACHASHES_number",
           'CALL_TOTAL_min',
           "CALL_incoming_min",
           "CALL_outgoing_min",
           "CALL_TOTAL_number",                                                   
           "CALL_incoming_number",                                                
           "CALL_outgoing_number",                                               
           "CALL_UNIQUE_CONTACTS_number",                                         
           "LIGHT_LUX_mean",                                                      
           "LIGHT_LUX_std",                                                       
           "SCREEN_onLocked_number" ,                                             
           "SCREEN_onUnlocked_number", 
           "SMS_received_number" ,                                                
           "SMS_sent_number" ,                                                    
           "SMS_UNIQUE_CONTACTS_number" 
      ),
      selected = "Cluster_HOME_min"
    ),
    plotOutput("Plot")
  ),
  
  server = function(input, output) {
    toListen <- reactive({
    list(input$Participant,input$PassiveMeasure)
  })
    observeEvent(toListen(),{
      Pnumber = input$Participant
      Feature <- input$PassiveMeasure
            
            
      Affect_Passive$timescale_beforeESM <- ordered(Affect_Passive$timescale_beforeESM,levels = c("1h","3h","6h","9h","12h","24h"))
      
      Affect_Passive$timescale_beforeESM_num <- recode(Affect_Passive$timescale_beforeESM, "1h" = 1, "3h" = 3,"6h" = 6,"9h" = 9,"12h" = 12, "24h" = 24 )
      
      Affect_Passive[,"Passivecopy"] <- Affect_Passive[,colnames(Affect_Passive) == Feature]
      
      plot0 <- ggplot(Affect_Passive[Affect_Passive$ParticipantNumber == Pnumber & Affect_Passive$timescale_beforeESM == "3h",]) +
        geom_line(aes(y = pa_mean, x = as.POSIXct(Date))) +
        theme_minimal() +
        xlab("") + 
        ylab("") +
        labs(color='') +
        ggtitle("Mean Positive Affect")
      
        plot1 <- ggplot(Affect_Passive[Affect_Passive$ParticipantNumber == Pnumber,]) +
        geom_line(aes(y = Passivecopy/timescale_beforeESM_num, x = as.POSIXct(Date), color = timescale_beforeESM)) +
        theme_minimal() +
        xlab("") + 
        ylab("") +
        labs(color='') +
        ggtitle(paste(Feature, "(Standardized)"))
      
      
      plot2 <- ggplot(Affect_Passive[Affect_Passive$ParticipantNumber == Pnumber,], aes(x=timescale_beforeESM, y=Passivecopy/timescale_beforeESM_num, fill = timescale_beforeESM, color = timescale_beforeESM)) + 
    geom_violin(alpha = 0.5) +
    geom_point(position = position_jitter(seed = 1, width = 0.2)) +
    theme_minimal() +
    xlab("") + 
    ylab("") +
    labs(fill='', color = '') 
      
      plot <- ggarrange(plot0, plot1, plot2, ncol = 1, common.legend = TRUE, legend = "right") 
#      annotate_figure(plot, left = textGrob(paste(Feature), rot = 90, vjust = 1, gp = gpar(cex = 1)))
      
    
       
      output$Plot = renderPlot({plot},  height = 800, width = 800)
      
    })
  },
  options = list(height = 1200, width = 820)
)
```

### NEW EXAMPLE 1: Correlations


```{r include=FALSE}
#Here we calculate the different Correlations

source("Calculation Correlation.R")

# Missing values labeled single sensor specific
CorrelationSampleTrue <- calculateCorr_pa(Affect_Passive)
CorrelationSampleTrue_18 <- calculateCorr_pa(Affect_Passive_18m)
CorrelationSampleTrue_12 <- calculateCorr_pa(Affect_Passive_12m)

# If one sensor is missing, all are missing
CorrelationSampleTrue_allNA <- calculateCorr_pa(Affect_Passive_allsensor_NA)
CorrelationSampleTrue_allNA_18 <- calculateCorr_pa(Affect_Passive_allsensor_NA_18m)
CorrelationSampleTrue_allNA_12 <- calculateCorr_pa(Affect_Passive_allsensor_NA_12m)


# No exclusion
CorrelationSampleTrue_noNA <- calculateCorr_pa(Affect_Passive_no_NA)

```

In the next lines of code I did the calculation for the paper

```{r eval=FALSE, include=FALSE}
CorrelationSampleTrue[CorrelationSampleTrue$ParticipantNumber == 117119 & CorrelationSampleTrue$Feature == "Cluster_HOME_min",]

CorrelationSampleTrue[CorrelationSampleTrue$ParticipantNumber == 117130 & CorrelationSampleTrue$Feature == "CALL_TOTAL_min",] #Sensor specific?/ No exclusion

### Missing Values all na
CorrelationSampleTrue_allNA[CorrelationSampleTrue_allNA$ParticipantNumber == 117119 & CorrelationSampleTrue_allNA$Feature == "Cluster_HOME_min",]

CorrelationSampleTrue_allNA[CorrelationSampleTrue_allNA$ParticipantNumber == 117130 & CorrelationSampleTrue_allNA$Feature == "CALL_TOTAL_min",]

### Missing Values 
CorrelationSampleTrue_noNA[CorrelationSampleTrue_noNA$ParticipantNumber == 117119 & CorrelationSampleTrue_noNA$Feature == "Cluster_HOME_min",]

CorrelationSampleTrue_noNA[CorrelationSampleTrue_noNA$ParticipantNumber == 117130 & CorrelationSampleTrue_noNA$Feature == "CALL_TOTAL_min",]

```

Plots Poster:
```{r eval=FALSE, include=FALSE}
### Always check if ordered factor is correct ####

##### Exclude Missing Values sensor specific

cor1a = CorrelationSampleTrue[CorrelationSampleTrue$ParticipantNumber %in% c(117119),] %>% filter(., Feature == "Cluster_HOME_min") %>% 
          ggplot(.,
               aes(
                 y = as.factor(Feature),
                 x = as.factor(timescale_beforeESM),
                 fill = Correlation
               )) +
  geom_tile() +
  scale_fill_gradient2(low = "#440154", mid = "white", high = "#21918c", limits =  c(-0.5,0.5)) +
  geom_text(aes(label = star), color = "black", size = 6) +
  ylab("Exclusion: 24h") +
  xlab("") +
#  ggtitle(paste("Labeling missing data: sensor specific")) +
  theme_minimal() +
theme(axis.text.y = element_text(size= 0))  

cor1a_18 = CorrelationSampleTrue_18[CorrelationSampleTrue_18$ParticipantNumber %in% c(117119),] %>% filter(., Feature == "Cluster_HOME_min") %>% 
          ggplot(.,
               aes(
                 y = as.factor(Feature),
                 x = as.factor(timescale_beforeESM),
                 fill = Correlation
               )) +
  geom_tile() +
  scale_fill_gradient2(low = "#440154", mid = "white", high = "#21918c", limits =  c(-0.5,0.5)) +
  geom_text(aes(label = star), color = "black", size = 6) +
  ylab("Exclusion: 18h") +
  xlab("") +
  theme_minimal() +
  theme(axis.text.y = element_text(size= 0))  

cor1a_12 = CorrelationSampleTrue_12[CorrelationSampleTrue_12$ParticipantNumber %in% c(117119),] %>% filter(., Feature == "Cluster_HOME_min") %>% 
          ggplot(.,
               aes(
                 y = as.factor(Feature),
                 x = as.factor(timescale_beforeESM),
                 fill = Correlation
               )) +
  geom_tile() +
  scale_fill_gradient2(low = "#440154", mid = "white", high = "#21918c", limits =  c(-0.5,0.5)) +
  geom_text(aes(label = star), color = "black", size = 6) +
  ylab("Exclusion: 12h") +
  xlab("") +
  theme_minimal() +
theme(axis.text.y = element_text(size= 0))  

plota <- ggarrange(cor1a,cor1a_18,cor1a_12,nrow =3, ncol = 1, common.legend = TRUE, legend = "right")

plota <- annotate_figure(plota, top = text_grob("Exclusion: One Measure Excluded",  size = 14))

##### Exclude Missing Values non-sensor specific

cor1b = CorrelationSampleTrue_allNA[CorrelationSampleTrue_allNA$ParticipantNumber %in% c(117119),] %>% filter(., Feature == "Cluster_HOME_min") %>% 
          ggplot(.,
               aes(
                 y = as.factor(Feature),
                 x = as.factor(timescale_beforeESM),
                 fill = Correlation
               )) +
  geom_tile() +
  scale_fill_gradient2(low = "#440154", mid = "white", high = "#21918c", limits =  c(-0.5,0.5)) +
  geom_text(aes(label = star), color = "black", size = 6) +
  ylab("Exclusion: 24h/18h") +
  xlab("") +
  theme_minimal() +
theme(axis.text.y = element_text(size= 0))  

blank <- grid.rect(gp=gpar(col="white"))

cor1b_12 = CorrelationSampleTrue_allNA_12[CorrelationSampleTrue_allNA_12$ParticipantNumber %in% c(117119),] %>% filter(., Feature == "Cluster_HOME_min") %>% 
          ggplot(.,
               aes(
                 y = as.factor(Feature),
                 x = as.factor(timescale_beforeESM),
                 fill = Correlation
               )) +
  geom_tile() +
  scale_fill_gradient2(low = "#440154", mid = "white", high = "#21918c", limits =  c(-0.5,0.5)) +
  geom_text(aes(label = star), color = "black", size = 6) +
  ylab("Exclusion: 12h") +
  xlab("") +
  theme_minimal() +
theme(axis.text.y = element_text(size= 0))  

    
plotb <- ggarrange(blank,cor1b,cor1b_12,nrow =3, ncol = 1, common.legend = TRUE, legend = "right")

plotb <- annotate_figure(plotb, top = text_grob("Exclusion: All Measures Excluded",  size = 14))

plot_home <- ggarrange(plota,plotb)

plot_home <- annotate_figure(plot_home, top = text_grob("Correlation Minutes being at Home & Positive Affect \n ",  size = 16))

###### Calls
##### Exclude Missing Values sensor specific

cor1a = CorrelationSampleTrue[CorrelationSampleTrue$ParticipantNumber %in% c(117130),] %>% filter(., Feature == "CALL_TOTAL_min") %>% 
          ggplot(.,
               aes(
                 y = as.factor(Feature),
                 x = as.factor(timescale_beforeESM),
                 fill = Correlation
               )) +
  geom_tile() +
  scale_fill_gradient2(low = "#440154", mid = "white", high = "#21918c", limits =  c(-0.5,0.5)) +
  geom_text(aes(label = star), color = "black", size = 6) +
  ylab("No Exclusion") +
  xlab("") +
#  ggtitle(paste("Labeling missing data: sensor specific")) +
  theme_minimal() +
theme(axis.text.y = element_text(size= 0))  

plota <- ggarrange(cor1a,nrow =2, ncol = 1, common.legend = TRUE, legend = "right")

plota <- annotate_figure(plota, top = text_grob("Exclusion: One Measure Excluded",  size = 14))

##### Exclude Missing Values non-sensor specific

cor1b = CorrelationSampleTrue_allNA[CorrelationSampleTrue_allNA$ParticipantNumber %in% c(117130),] %>% filter(., Feature == "CALL_TOTAL_min") %>% 
          ggplot(.,
               aes(
                 y = as.factor(Feature),
                 x = as.factor(timescale_beforeESM),
                 fill = Correlation
               )) +
  geom_tile() +
  scale_fill_gradient2(low = "#440154", mid = "white", high = "#21918c", limits =  c(-0.5,0.5)) +
  geom_text(aes(label = star), color = "black", size = 6) +
  ylab("Exclusion: 24h/18h") +
  xlab("") +
  theme_minimal() +
theme(axis.text.y = element_text(size= 0))  

cor1b_12 = CorrelationSampleTrue_allNA_12[CorrelationSampleTrue_allNA_12$ParticipantNumber %in% c(117130),] %>% filter(., Feature == "CALL_TOTAL_min") %>% 
          ggplot(.,
               aes(
                 y = as.factor(Feature),
                 x = as.factor(timescale_beforeESM),
                 fill = Correlation
               )) +
  geom_tile() +
  scale_fill_gradient2(low = "#440154", mid = "white", high = "#21918c", limits =  c(-0.5,0.5)) +
  geom_text(aes(label = star), color = "black", size = 6) +
  ylab("Exclusion: 12h") +
  xlab("") +
  theme_minimal() +
theme(axis.text.y = element_text(size= 0))  

    
plotb <- ggarrange(cor1b,cor1b_12,nrow =2, ncol = 1, common.legend = TRUE, legend = "right")

plotb <- annotate_figure(plotb, top = text_grob("Exclusion: All Measures Excluded",  size = 14))

plot_calling <- ggarrange(plota,plotb)

plot_calling <- annotate_figure(plot_calling, top = text_grob("Correlation Minutes of Calling & Positive Affect \n",  size = 14))

ggsave(
  "plot_home.jpg",
  plot = plot_home,
  width = 29,
  height =12,
  units = c("cm"),
  dpi = 300,
  limitsize = TRUE,
  bg = NULL)


ggsave(
  "plot_calling.jpg",
  plot = plot_calling,
  width = 26,
  height =12*(2/3),
  units = c("cm"),
  dpi = 300,
  limitsize = TRUE,
  bg = NULL)
```

Shiny App for other features (supplementary material?)
```{r echo=FALSE}

shinyApp(
  ui = fluidPage(
    selectInput(
      "Participant",
      label = "Participant: ",
      choices = c(117113,117114,117119,117121,117130,117129,117131,117134,117135,117137,"Overall"),
      selected = 117113
    ),selectInput(
      "Affect",
      label = "Affect: ",
      choices = c(
        'pa_mean',
        'na_mean'
      ),
      selected = "pa_mean"
    ),
    plotOutput("Plot")
  ),
  
  server = function(input, output) {
    toListen <- reactive({
    list(input$Participant,input$Affect)
  })
    observeEvent(toListen(),{
      Pnumber = input$Participant
      Feature <- input$Affect

      if(Feature == "pa_mean"){
      CorrelationSampleTrue <- CorrelationSampleTrue
      }else{
        CorrelationSampleTrue <- CorrelationSampleTrue_na
      }
      
      cor1 =  ggplot(CorrelationSampleTrue[CorrelationSampleTrue$ParticipantNumber == Pnumber, ],
                     aes(
                       y = as.factor(Feature),
                       x = as.factor(timescale_beforeESM),
                       fill = Correlation
                     )) +
        geom_tile() +
        scale_fill_gradient2(low = "#D7191C", mid = "white", high = "#2C7BB6", limits =  c(-0.5,0.5)) +
        geom_text(aes(label = star), color = "black", size = 4) +
        ylab("") +
        xlab("") +
        ggtitle(paste("Correlation")) +
        theme_minimal()
    
 
      output$Plot = renderPlot({cor1},  height = 800, width = 800)
      
    })
  },
  options = list(height = 1200, width = 820)
)
```


### OLD EXAMPLE 1: Correlations (old before changing missing values)


```{r include=FALSE}
#Here we calculate the different Correlations

source("Calculation Correlation.R")

# Missing values labeled single sensor specific
CorrelationSampleTrue <- calculateCorr_pa(Affect_Passive)
CorrelationSampleTrue_na <- calculateCorr_na(Affect_Passive)

# If one sensor is missing, all are missing
CorrelationSampleTrue_allNA <- calculateCorr_pa(Affect_Passive_allsensor_NA)
CorrelationSampleTrue_allNA$diff <- abs(CorrelationSampleTrue$Correlation - CorrelationSampleTrue_allNA$Correlation)

CorrelationSampleTrue_allNA$diff_sign = ""
CorrelationSampleTrue_allNA$diff_sign[CorrelationSampleTrue$sign != CorrelationSampleTrue_allNA$sign] = "x"


CorrelationSampleTrue_na_allNA <- calculateCorr_na(Affect_Passive_allsensor_NA)
CorrelationSampleTrue_na_allNA$diff <- abs(CorrelationSampleTrue_na$Correlation - CorrelationSampleTrue_na_allNA$Correlation)

CorrelationSampleTrue_na_allNA$diff_sign = ""
CorrelationSampleTrue_na_allNA$diff_sign[CorrelationSampleTrue_na$sign != CorrelationSampleTrue_na_allNA$sign] = "x"

# No missing values labeled
CorrelationSampleTrue_noNA <- calculateCorr_pa(Affect_Passive_no_NA)
CorrelationSampleTrue_noNA$diff <- abs(CorrelationSampleTrue$Correlation - CorrelationSampleTrue_noNA$Correlation)

CorrelationSampleTrue_noNA$diff_sign = ""
CorrelationSampleTrue_noNA$diff_sign[CorrelationSampleTrue$sign != CorrelationSampleTrue_noNA$sign] = "x"

CorrelationSampleTrue_na_noNA <- calculateCorr_na(Affect_Passive_no_NA)
CorrelationSampleTrue_na_noNA$diff <- abs(CorrelationSampleTrue_na$Correlation - CorrelationSampleTrue_na_noNA$Correlation)

CorrelationSampleTrue_na_noNA$diff_sign = ""
CorrelationSampleTrue_na_noNA$diff_sign[CorrelationSampleTrue_na$sign != CorrelationSampleTrue_na_noNA$sign] = "x"



```

In the next lines of code I did the calculation for the paper

```{r eval=FALSE, include=FALSE}
CorrelationSampleTrue[CorrelationSampleTrue$ParticipantNumber == 117119 & CorrelationSampleTrue$Feature == "Cluster_HOME_min",]

CorrelationSampleTrue[CorrelationSampleTrue$ParticipantNumber == 117130 & CorrelationSampleTrue$Feature == "CALL_TOTAL_min",]

### Missing Values all na
CorrelationSampleTrue_allNA[CorrelationSampleTrue_allNA$ParticipantNumber == 117119 & CorrelationSampleTrue_allNA$Feature == "Cluster_HOME_min",]

CorrelationSampleTrue_allNA[CorrelationSampleTrue_allNA$ParticipantNumber == 117130 & CorrelationSampleTrue_allNA$Feature == "CALL_TOTAL_min",]

### Missing Values 
CorrelationSampleTrue_noNA[CorrelationSampleTrue_noNA$ParticipantNumber == 117119 & CorrelationSampleTrue_noNA$Feature == "Cluster_HOME_min",]

CorrelationSampleTrue_noNA[CorrelationSampleTrue_noNA$ParticipantNumber == 117130 & CorrelationSampleTrue_noNA$Feature == "CALL_TOTAL_min",]

```

Here I did the plots for the paper

```{r eval=FALSE, include=FALSE}

### Always check if ordered factor is correct ####
cor1a = CorrelationSampleTrue[CorrelationSampleTrue$ParticipantNumber %in% c(117119),] %>% filter(., Feature == "Cluster_HOME_min") %>% 
          ggplot(.,
               aes(
                 y = as.factor(Feature),
                 x = as.factor(timescale_beforeESM),
                 fill = Correlation
               )) +
  geom_tile() +
  scale_fill_gradient2(low = "#D7191C", mid = "white", high = "#2C7BB6", limits =  c(-0.5,0.5)) +
  geom_text(aes(label = star), color = "black", size = 4) +
  ylab("") +
  xlab("") +
  ggtitle(paste("Correlation positive affect & minutes being at home a) exclusion sensor specific")) +
  theme_minimal() +
theme(axis.text.y = element_text(size= 0))  

 cor1b = CorrelationSampleTrue[CorrelationSampleTrue$ParticipantNumber %in% c(117130),] %>% filter(., Feature == "CALL_TOTAL_min") %>% 
              ggplot(.,
                   aes(
                     y = as.factor(Feature),
                     x = as.factor(timescale_beforeESM),
                     fill = Correlation
                   )) +
      geom_tile() +
      scale_fill_gradient2(low = "#D7191C", mid = "white", high = "#2C7BB6", limits =  c(-0.5,0.5)) +
      geom_text(aes(label = star), color = "black", size = 4) +
      ylab("") +
      xlab("") +
      ggtitle(paste("Correlation positive affect & minutes of calling b) exclusion non-sensor specific")) +
      theme_minimal() +
theme(axis.text.y = element_text(size= 0))  
  

 cor2a =  CorrelationSampleTrue_allNA[CorrelationSampleTrue_allNA$ParticipantNumber  %in% c(117119),] %>% filter(., Feature == "Cluster_HOME_min") %>% 
                ggplot(.,
                     aes(
                       y = as.factor(Feature),
                       x = as.factor(timescale_beforeESM),
                       fill = Correlation
                     )) +
        geom_tile() +
        scale_fill_gradient2(low = "#D7191C", mid = "white", high = "#2C7BB6", limits =  c(-0.5,0.5)) +
        geom_text(aes(label = star), color = "black", size = 4) +
        ylab("") +
        xlab("") +
        ggtitle(paste("Correlation positive affect & minutes being at home b) exclusion non-sensor specific")) +
        theme_minimal() +
 labs(fill="Correlation") +
  theme(axis.text.y = element_text(size= 0))  
 
  cor2b =  CorrelationSampleTrue_allNA[CorrelationSampleTrue_allNA$ParticipantNumber  %in% c(117130),] %>% filter(., Feature == "CALL_TOTAL_min") %>% 
                ggplot(.,
                     aes(
                       y = as.factor(Feature),
                       x = as.factor(timescale_beforeESM),
                       fill = Correlation
                     )) +
        geom_tile() +
        scale_fill_gradient2(low = "#D7191C", mid = "white", high = "#2C7BB6", limits =  c(-0.5,0.5)) +
        geom_text(aes(label = star), color = "black", size = 4) +
        ylab("") +
        xlab("") +
        ggtitle(paste("Correlation positive affect & minutes of calling c) no exclusion")) +
        theme_minimal() +
 labs(fill="Correlation") +
  theme(axis.text.y = element_text(size= 0))  
 
 
 

cor3a =  CorrelationSampleTrue_noNA[CorrelationSampleTrue_noNA$ParticipantNumber  %in% c(117119),] %>% filter(., Feature == "Cluster_HOME_min" ) %>%  
          ggplot(.,
               aes(
                 y = as.factor(Feature),
                 x = as.factor(timescale_beforeESM),
                 fill = Correlation
               )) +
  geom_tile() +
  scale_fill_gradient2(low = "#D7191C", mid = "white", high = "#2C7BB6", limits =  c(-0.5,0.5)) +
  geom_text(aes(label = star), color = "black", size = 4) +
  ylab("") +
  xlab("") +
  ggtitle(paste("Correlation positive affect & minutes of being at home c) no exclusion")) +
  theme_minimal() +
  labs(fill="Correlation") +
theme(axis.text.y = element_text(size= 0))  

      

      
plota <- ggarrange(cor1a,cor1b,cor2a,cor2b,cor3a,nrow =3, ncol = 2, common.legend = FALSE)


ggsave(
  "Correlation_new.jpg",
  plot = plota,
  width = 30,
  height = 12,
  units = c("cm"),
  dpi = 300,
  limitsize = TRUE,
  bg = NULL)

```

PlotsnPoster:
```{r eval=FALSE, include=FALSE}

### Always check if ordered factor is correct ####
cor1a = CorrelationSampleTrue[CorrelationSampleTrue$ParticipantNumber %in% c(117119),] %>% filter(., Feature == "Cluster_HOME_min") %>% 
          ggplot(.,
               aes(
                 y = as.factor(Feature),
                 x = as.factor(timescale_beforeESM),
                 fill = Correlation
               )) +
  geom_tile() +
  scale_fill_gradient2(low = "#440154", mid = "white", high = "#21918c", limits =  c(-0.5,0.5)) +
  geom_text(aes(label = star), color = "black", size = 6) +
  ylab("") +
  xlab("") +
  ggtitle(paste("Correlation positive affect & minutes being at home \n (exclusion sensor specific)")) +
  theme_minimal() +
theme(axis.text.y = element_text(size= 0))  

 cor1b = CorrelationSampleTrue[CorrelationSampleTrue$ParticipantNumber %in% c(117130),] %>% filter(., Feature == "CALL_TOTAL_min") %>% 
              ggplot(.,
                   aes(
                     y = as.factor(Feature),
                     x = as.factor(timescale_beforeESM),
                     fill = Correlation
                   )) +
      geom_tile() +
      scale_fill_gradient2(low = "#440154", mid = "white", high = "#21918c", limits =  c(-0.5,0.5)) +
      geom_text(aes(label = star), color = "black", size = 6) +
      ylab("") +
      xlab("") +
      ggtitle(paste("Correlation positive affect & minutes of calling \n (exclusion non sensor specific)")) +
      theme_minimal() +
theme(axis.text.y = element_text(size= 0))  
  

 cor2a =  CorrelationSampleTrue_allNA[CorrelationSampleTrue_allNA$ParticipantNumber  %in% c(117119),] %>% filter(., Feature == "Cluster_HOME_min") %>% 
                ggplot(.,
                     aes(
                       y = as.factor(Feature),
                       x = as.factor(timescale_beforeESM),
                       fill = Correlation
                     )) +
        geom_tile() +
        scale_fill_gradient2(low = "#440154", mid = "white", high = "#21918c", limits =  c(-0.5,0.5)) +
        geom_text(aes(label = star), color = "black", size = 6) +
        ylab("") +
        xlab("") +
        ggtitle(paste("Correlation positive affect & minutes being at home \n (exclusion non sensor specific)")) +
        theme_minimal() +
 labs(fill="Correlation") +
  theme(axis.text.y = element_text(size= 0))  
 
  cor2b =  CorrelationSampleTrue_allNA[CorrelationSampleTrue_allNA$ParticipantNumber  %in% c(117130),] %>% filter(., Feature == "CALL_TOTAL_min") %>% 
                ggplot(.,
                     aes(
                       y = as.factor(Feature),
                       x = as.factor(timescale_beforeESM),
                       fill = Correlation
                     )) +
        geom_tile() +
        scale_fill_gradient2(low = "#440154", mid = "white", high = "#21918c", limits =  c(-0.5,0.5)) +
        geom_text(aes(label = star), color = "black", size = 6) +
        ylab("") +
        xlab("") +
        ggtitle(paste("Correlation positive affect & minutes of calling \n (no exclusion)")) +
        theme_minimal() +
 labs(fill="Correlation") +
  theme(axis.text.y = element_text(size= 0))  
 
 
 

cor3a =  CorrelationSampleTrue_noNA[CorrelationSampleTrue_noNA$ParticipantNumber  %in% c(117119),] %>% filter(., Feature == "Cluster_HOME_min" ) %>%  
          ggplot(.,
               aes(
                 y = as.factor(Feature),
                 x = as.factor(timescale_beforeESM),
                 fill = Correlation
               )) +
  geom_tile() +
  scale_fill_gradient2(low = "#440154", mid = "white", high = "#21918c", limits =  c(-0.5,0.5)) +
  geom_text(aes(label = star), color = "black", size = 6) +
  ylab("") +
  xlab("") +
  ggtitle(paste("Correlation positive affect & minutes of being at home \n (no exclusion)")) +
  theme_minimal() +
  labs(fill="Correlation") +
theme(axis.text.y = element_text(size= 0))  

      

      
plota <- ggarrange(cor1a,cor1b,cor2a,cor2b,cor3a,nrow =3, ncol = 2, common.legend = FALSE)


ggsave(
  "Correlation_new_poster.jpg",
  plot = plota,
  width = 29,
  height =13,
  units = c("cm"),
  dpi = 300,
  limitsize = TRUE,
  bg = NULL)

```

Shiny App for other features (supplementary material?)
```{r echo=FALSE}

shinyApp(
  ui = fluidPage(
    selectInput(
      "Participant",
      label = "Participant: ",
      choices = c(117113,117114,117119,117121,117130,117129,117131,117134,117135,117137,"Overall"),
      selected = 117113
    ),selectInput(
      "Affect",
      label = "Affect: ",
      choices = c(
        'pa_mean',
        'na_mean'
      ),
      selected = "pa_mean"
    ),
    plotOutput("Plot")
  ),
  
  server = function(input, output) {
    toListen <- reactive({
    list(input$Participant,input$Affect)
  })
    observeEvent(toListen(),{
      Pnumber = input$Participant
      Feature <- input$Affect

      if(Feature == "pa_mean"){
      CorrelationSampleTrue <- CorrelationSampleTrue
      }else{
        CorrelationSampleTrue <- CorrelationSampleTrue_na
      }
      
      cor1 =  ggplot(CorrelationSampleTrue[CorrelationSampleTrue$ParticipantNumber == Pnumber, ],
                     aes(
                       y = as.factor(Feature),
                       x = as.factor(timescale_beforeESM),
                       fill = Correlation
                     )) +
        geom_tile() +
        scale_fill_gradient2(low = "#D7191C", mid = "white", high = "#2C7BB6", limits =  c(-0.5,0.5)) +
        geom_text(aes(label = star), color = "black", size = 4) +
        ylab("") +
        xlab("") +
        ggtitle(paste("Correlation")) +
        theme_minimal()
    
 
      output$Plot = renderPlot({cor1},  height = 800, width = 800)
      
    })
  },
  options = list(height = 1200, width = 820)
)
```


### EXAMPLE 2: Prediciton Models (for affect, because here we can do individualized models?)
As a next step I want to build simple prediciton models. 
Nick: non-stationarity, maybe at the beginning relationship there but then not, How to deal with this
Cross-validation (with time, rolling window) (look at nicks code)

```{r eval=FALSE, include=FALSE}
set.seed(12361488)
library(caret)

#Calculated with the script: ParallelComputingML.R

OverallResults_1h <- read.csv("OverallResults_1h.csv")
OverallResults_3h <- read.csv("OverallResults_3h.csv")
OverallResults_6h <- read.csv("OverallResults_6h.csv")
OverallResults_9h <- read.csv("OverallResults_9h.csv")
OverallResults_12h <- read.csv("OverallResults_12h.csv")
OverallResults_24h <- read.csv("OverallResults_24h.csv")


#### Calculate Performance Measures ####
perfromanceCalc <- function(OverallResults){
counter = 0
OverallResults <- OverallResults[OverallResults$index >= 43,]
for(i in unique(OverallResults$w)){
counter = counter + 1
results <- OverallResults[OverallResults$w == i,]

cor = cor.test(results$pred,results$true)$estimate
cor.int_1 = cor.test(results$pred,results$true)$conf.int[1]
cor.int_2 = cor.test(results$pred,results$true)$conf.int[2]
rss <- sum((results$pred - results$true) ^ 2)  ## residual sum of squares
tss <- sum((results$true - mean(results$true)) ^ 2)  ## total sum of squares
rsq <- 1 - rss/tss
RMSE <- RMSE(results$pred,results$true)
postResample(results$pred,results$true)

if(counter == 1){
resultsPerformance <- cbind(i,cor,cor.int_1,cor.int_2,rsq,RMSE)
OverallResultsPerformance <- resultsPerformance
}else{
resultsPerformance <- cbind(i,cor,cor.int_1,cor.int_2,rsq,RMSE)
OverallResultsPerformance <- rbind(OverallResultsPerformance, resultsPerformance)
}
OverallResultsPerformance <- as.data.frame(OverallResultsPerformance)
}
return(OverallResultsPerformance)
}

OverallResultsPerformance_1h <- perfromanceCalc(OverallResults_1h)
OverallResultsPerformance_3h <- perfromanceCalc(OverallResults_3h)
OverallResultsPerformance_6h <- perfromanceCalc(OverallResults_6h)
OverallResultsPerformance_9h <- perfromanceCalc(OverallResults_9h)
OverallResultsPerformance_12h <- perfromanceCalc(OverallResults_12h)
OverallResultsPerformance_24h <- perfromanceCalc(OverallResults_24h)


plot2 <- ggplot() +
   geom_line(aes(y = OverallResultsPerformance_1h$rsq, x = OverallResultsPerformance_1h$i/6, color = "1h")) +
  geom_line(aes(y = OverallResultsPerformance_3h$rsq, x = OverallResultsPerformance_3h$i/6, color = "3h")) +
  geom_line(aes(y = OverallResultsPerformance_6h$rsq, x = OverallResultsPerformance_6h$i/6, color = "6h")) +
    geom_line(aes(y = OverallResultsPerformance_9h$rsq, x = OverallResultsPerformance_9h$i/6, color = "9h")) +
     geom_line(aes(y = OverallResultsPerformance_12h$rsq, x = OverallResultsPerformance_12h$i/6, color = "12h")) +
     geom_line(aes(y = OverallResultsPerformance_24h$rsq, x = OverallResultsPerformance_24h$i/6, color = "24h")) +
  theme_minimal() +
  xlab("Moving Window Size (in days)") +
  ylab("R-squared") +
 scale_color_viridis(discrete=TRUE,limits = c("1h","3h","6h","9h","12h","24h")) +
  labs(color = "Level of Aggregation") + 
  # Annotation
  annotate(
    geom = "curve", x = 6/6, y = 0.285, xend = 6/6, yend = 0.1, 
    curvature = .2,  colour = "#909090", arrow = arrow(length = unit(2, "mm"))
  ) +
  annotate(geom = "text", colour = "#838383", x = 6.1/6, y = 0.07, label = "Data aggregated one hour before ESM \noverall leads to worse predictions \ncompared to broader time scales.", hjust = "left") +
   annotate(
    geom = "curve", colour = "#909090", x = 35/6, y = 0.065, xend = 28/6, yend = 0.029, 
    curvature = .2, arrow = arrow(length = unit(2, "mm"))
  ) +
  annotate(geom = "text", colour = "#838383", x = 22/6, y = 0.01, label = "The prediction accuracy further decreases \nfor choosing larger moving window sizes.", hjust = "left") +
  theme(legend.text = element_text(size=11))

 ggsave(
 "RSquared.jpg",
 plot = plot2,
 width = 23,
 height = 10,
 units = c("cm"),
 dpi = 300,
 limitsize = TRUE,
 bg = NULL)


plot3 <- ggplot() +
   geom_line(aes(y = OverallResultsPerformance_1h$cor, x = OverallResultsPerformance_1h$i, color = "1h")) +
  geom_line(aes(y = OverallResultsPerformance_3h$cor, x = OverallResultsPerformance_3h$i, color = "3h")) +
  geom_line(aes(y = OverallResultsPerformance_6h$cor, x = OverallResultsPerformance_6h$i, color = "6h")) +
    geom_line(aes(y = OverallResultsPerformance_9h$cor, x = OverallResultsPerformance_9h$i, color = "9h")) +
     geom_line(aes(y = OverallResultsPerformance_12h$cor, x = OverallResultsPerformance_12h$i, color = "12h")) +
     geom_line(aes(y = OverallResultsPerformance_24h$cor, x = OverallResultsPerformance_24h$i, color = "24h")) +
  theme_minimal() +
  xlab("Moving Window Size") +
  ylab("Correlation") +
 scale_color_viridis(discrete=TRUE,limits = c("1h","3h","6h","9h","12h","24h")) +
  labs(color = "Level of Aggregation")
```

Paper report Rsquared and confidence
```{r eval=FALSE, include=FALSE}
#### Level of Aggregation

#Correlation 1h
max <- which(OverallResultsPerformance_1h$rsq == max(OverallResultsPerformance_1h$rsq))
min <- which(OverallResultsPerformance_1h$rsq == min(OverallResultsPerformance_1h$rsq))

paste("(m = ",round(mean(OverallResultsPerformance_1h$rsq),2), ", max = ",round(OverallResultsPerformance_1h$rsq[max],2),", min = ",round(OverallResultsPerformance_1h$rsq[min],2),")", sep = "")

#Correlation 3h
max <- which(OverallResultsPerformance_3h$rsq == max(OverallResultsPerformance_3h$rsq))
min <- which(OverallResultsPerformance_3h$rsq == min(OverallResultsPerformance_3h$rsq))

paste("(m = ",round(mean(OverallResultsPerformance_3h$rsq),2), ", max = ",round(OverallResultsPerformance_3h$rsq[max],2),", min = ",round(OverallResultsPerformance_3h$rsq[min],2),")", sep = "")

#Correlation 6h
max <- which(OverallResultsPerformance_6h$cor == max(OverallResultsPerformance_6h$cor))
min <- which(OverallResultsPerformance_6h$cor == min(OverallResultsPerformance_6h$cor))

paste("(m = ",round(mean(OverallResultsPerformance_6h$rsq),2), ", max = ",round(OverallResultsPerformance_6h$rsq[max],2),", min = ",round(OverallResultsPerformance_6h$rsq[min],2),")", sep = "")

#Correlation 9h
max <- which(OverallResultsPerformance_9h$rsq == max(OverallResultsPerformance_9h$rsq))
min <- which(OverallResultsPerformance_9h$rsq == min(OverallResultsPerformance_9h$rsq))

paste("(m = ",round(mean(OverallResultsPerformance_9h$rsq),2), ", max = ",round(OverallResultsPerformance_9h$rsq[max],2),", min = ",round(OverallResultsPerformance_9h$rsq[min],2),")", sep = "")

#Correlation 12h
max <- which(OverallResultsPerformance_12h$rsq == max(OverallResultsPerformance_12h$rsq))
min <- which(OverallResultsPerformance_12h$rsq == min(OverallResultsPerformance_12h$rsq))


paste("(m = ",round(mean(OverallResultsPerformance_12h$rsq),2), ", max = ",round(OverallResultsPerformance_12h$rsq[max],2),", min = ",round(OverallResultsPerformance_12h$rsq[min],2),")", sep = "")

#Correlation 24h
max <- which(OverallResultsPerformance_24h$rsq == max(OverallResultsPerformance_24h$rsq))
min <- which(OverallResultsPerformance_24h$rsq == min(OverallResultsPerformance_24h$rsq))

paste("(m = ",round(mean(OverallResultsPerformance_24h$rsq),2), ", max = ",round(OverallResultsPerformance_24h$rsq[max],2),", min = ",round(OverallResultsPerformance_24h$rsq[min],2),")", sep = "")






#### Moving Window
##1h
#Lowest window
paste("(R-Squared = ",round(OverallResultsPerformance_1h$rsq[1],2),")", sep = "")

#highest window
paste("(R-Squared = ",round(OverallResultsPerformance_1h$rsq[37],2),")", sep = "")

##24h
#Lowest window
paste("(R-Squared = ",round(OverallResultsPerformance_24h$rsq[1],2),")", sep = "")

#highest window
paste("(R-Squared = ",round(OverallResultsPerformance_24h$rsq[37],2),")", sep = "")

```

Supplementary Material:
- Maybe actual predictions for different time windows
```{r eval=FALSE, include=FALSE}
plot <- OverallResults_24h %>%  gather(., Prediction, Value, pred:true) %>% 
ggplot(., (aes(y = Value, x = index,color = Prediction ))) +
  geom_line() +
  xlab("") +
  ylab("") +
  facet_wrap( ~ w) 

ggsave(
  "predictions.jpg",
  plot = plot,
  width = 30,
  height = 12,
  units = c("cm"),
  dpi = 300,
  limitsize = TRUE,
  bg = NULL)


plot3 <- OverallResults_24h[OverallResults_24h$w %in% c(6,10,20,30,42) & OverallResults_24h$index >= 43,] %>% 
ggplot(.) +
  geom_line(aes(y = true, x = index )) +
  geom_line(aes(y = pred, x = index, color = as.factor(w))) +
  xlab("") +
  ylab("") +
  theme_minimal()


ggsave(
  "Predictions_windows.jpg",
  plot = plot3,
  width = 30,
  height = 12,
  units = c("cm"),
  dpi = 300,
  limitsize = TRUE,
  bg = NULL)

#00798c,d1495b,edae49,66a182,2e4057,8d96a3

ggplot() +
   geom_line(aes(y = OverallResultsPerformance_1h$cor, x = OverallResultsPerformance_1h$i, color = "1h")) +
  geom_line(aes(y = OverallResultsPerformance_3h$cor, x = OverallResultsPerformance_3h$i, color = "3h")) +
  geom_line(aes(y = OverallResultsPerformance_6h$cor, x = OverallResultsPerformance_6h$i, color = "6h")) +
    geom_line(aes(y = OverallResultsPerformance_9h$cor, x = OverallResultsPerformance_9h$i, color = "9h")) +
     geom_line(aes(y = OverallResultsPerformance_12h$cor, x = OverallResultsPerformance_12h$i, color = "12h")) +
     geom_line(aes(y = OverallResultsPerformance_24h$cor, x = OverallResultsPerformance_24h$i, color = "24h")) +
  theme_minimal() +
  xlab("Moving Window Size") +
  ylab("Correlation") +
 scale_color_viridis(discrete=TRUE,limits = c("1h","3h","6h","9h","12h","24h")) +
  labs(color = "Level of aggregation")


ggplot() +
   geom_line(aes(y = OverallResultsPerformance_1h$RMSE, x = OverallResultsPerformance_1h$i, color = "1h")) +
  geom_line(aes(y = OverallResultsPerformance_3h$RMSE, x = OverallResultsPerformance_3h$i, color = "3h")) +
  geom_line(aes(y = OverallResultsPerformance_6h$RMSE, x = OverallResultsPerformance_6h$i, color = "6h")) +
    geom_line(aes(y = OverallResultsPerformance_9h$RMSE, x = OverallResultsPerformance_9h$i, color = "9h")) +
     geom_line(aes(y = OverallResultsPerformance_12h$RMSE, x = OverallResultsPerformance_12h$i, color = "12h")) +
     geom_line(aes(y = OverallResultsPerformance_24h$RMSE, x = OverallResultsPerformance_24h$i, color = "24h")) +
  theme_minimal() +
  xlab("Moving Window Size") +
  ylab("RMSE") +
 scale_color_viridis(discrete=TRUE,limits = c("1h","3h","6h","9h","12h","24h")) +
  labs(color = "Level of aggregation")


```


### NOT INCLUDE IN PAPER: Things after supervision meeting
```{r eval=FALSE, include=FALSE}
library(forecast)
library(fpp2)

ggAcf(Participant1$pa_mean, lag.max = 20) +
  theme_minimal()

ggCcf(Participant1$pa_mean,Participant1$Cluster_HOME_min, lag.max = 20) +
  theme_minimal()


Participant1 = Affect_Passive[Affect_Passive["ParticipantNumber"] == 117134 & Affect_Passive["timescale_beforeESM"] == "1h",  ]

runcor1h <- runner(data.frame(Participant1$pa_mean, Participant1$APP_USAGE_min), k = 40, function(x) cor.test(x[,1], x[,2], na.rm = TRUE)$estimate, na_pad = TRUE)

runp1h <- runner(data.frame(Participant1$pa_mean, Participant1$APP_USAGE_min), k = 40, function(x) cor.test(x[,1], x[,2], na.rm = TRUE)$p.value, na_pad = TRUE)

runp1h[runp1h > 0.05] <- NA 

Participant1 = Affect_Passive[Affect_Passive["ParticipantNumber"] == 117134 & Affect_Passive["timescale_beforeESM"] == "3h",  ]

runcor3h <- runner(data.frame(Participant1$pa_mean, Participant1$APP_USAGE_min), k = 40, function(x) cor.test(x[,1], x[,2], na.rm = TRUE)$estimate, na_pad = TRUE)

runp3h <- runner(data.frame(Participant1$pa_mean, Participant1$APP_USAGE_min), k = 40, function(x) cor.test(x[,1], x[,2], na.rm = TRUE)$p.value, na_pad = TRUE)

runp3h[runp3h > 0.05] <- NA 


Participant1 = Affect_Passive[Affect_Passive["ParticipantNumber"] == 117134 & Affect_Passive["timescale_beforeESM"] == "6h",  ]

runcor6h <- runner(data.frame(Participant1$pa_mean, Participant1$APP_USAGE_min), k = 40, function(x) cor.test(x[,1], x[,2], na.rm = TRUE)$estimate, na_pad = TRUE)

runp6h <- runner(data.frame(Participant1$pa_mean, Participant1$APP_USAGE_min), k = 40, function(x) cor.test(x[,1], x[,2], na.rm = TRUE)$p.value, na_pad = TRUE)

runp6h[runp6h > 0.05] <- NA 

Participant1 = Affect_Passive[Affect_Passive["ParticipantNumber"] == 117134 & Affect_Passive["timescale_beforeESM"] == "24h",  ]

runcor24h <- runner(data.frame(Participant1$pa_mean, Participant1$APP_USAGE_min), k = 40, function(x) cor.test(x[,1], x[,2], na.rm = TRUE)$estimate, na_pad = TRUE)

runp24h <- runner(data.frame(Participant1$pa_mean, Participant1$APP_USAGE_min), k = 40, function(x) cor.test(x[,1], x[,2], na.rm = TRUE)$p.value, na_pad = TRUE)

runp24h[runp24h > 0.05] <- NA 

ggplot() +
  geom_line(aes(y = runcor1h, x = 1:length(runcor),color = "1h_cor")) +
  geom_line(aes(y = runcor6h, x = 1:length(runcor),color = "6h_cor")) +
  geom_line(aes(y = runcor24h, x = 1:length(runcor),color = "24h_cor")) +
  geom_line(aes(y = runcor3h, x = 1:length(runcor),color = "3h_cor")) +
 # geom_hline(yintercept = 0.05) +
  geom_vline(xintercept = 42) +
  theme_minimal() +
  ylab("")

Participant1$weekend <- weekdays(as.POSIXct(Participant1$Date)) %in% c("Saturday", "Sunday")


ggplot(Participant1) +
  geom_bar(stat="Identity", aes(y=weekend*max(Cluster_HOME_min/30),x = as.POSIXct(Date)), col="yellow", alpha=.2, width = 1) +
 # geom_area(aes(y=weekend*max(Cluster_HOME_min/30), x = as.POSIXct(Date)),fill="#FDFD96") +
  geom_line(aes(y = pa_mean, x = as.POSIXct(Date), color = "pa_mean")) +
  geom_line(aes(y = Cluster_HOME_min/30, x = as.POSIXct(Date),color = "HOME")) +
  theme_minimal() +
  xlab("") + 
  ylab("") +
  labs(color='') 
```



